### 2018-02-15 doc.tex
Initial commit (copying roughly from failed overleaf)

\begin{abstract}

\mk{Unedited placeholder text}

\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) has led to recent 
calls for abandoning its use. We argue that statistical hypothesis tests are useful, but are not, and should not be 
referred to, as tests of significance. We propose that a sensible method to reduce misconceptions about p~values 
is to refer to the results of NHST (i.e. $p < or > 0.05$) using ``statistical clarity''. A test of the null hypothesis tells 
us whether or not we can \emph{clearly} see our effect (e.g. whether a correlation is positive or negative, or if a response 
in the treatment group is greater than the response in the control group). Specifically, we argue the use of ``statistical
clarity'' will help researchers avoid accepting the null hypothesis and retrieve the English definition for ``significance'' 
to shift focus back to substantive significance.

\textbf{Structure:} I like the idea of two parallel boxes that have examples of language used in published papers on the
left and corrected language on the right. Maybe three examples that correspond to four primary misinterpretations people
make (zero effect, large p-values as ``more'' evidence for something, difference between clear and not clear is not clear,
substantive significance)

\textbf{Previous Work:} The bottom line is that \emph{\textbf{a lot}} has been said on the general topic of NHST and 
p-values, though the idea of changing the language to clarity and retrieving the English definition of significant
is novel. \citet{Bernardietal.2017} and \citet{McShaneetal.2017} have covered a lot of the history that is
recounted below. It may be best to just cite these papers and state that concern about NHST and p-value abuse 
remains high. \citep{Bernardietal.2017} present an analysis of the presence of errors in the interpretation of 
results and ambiguity in language focused on NHST. Out of  They point out that these results are similar to the
results from a similar review in the field of economics \citep{ZiliakandMcCloskey2008}.

\textbf{Notes:} A lot of this language assumes $H_{0} = 0$. Probably need to address clearly that many of these cited
papers are based in psychology. I imagine we will want to anonymize quotes? (Though I kind of want to call out the null
result short courses paper --- maybe as a point about non-significance and calling for reform)

\textbf{Venue:} \mk{My list, no input from PIs on this yet}. No idea... Forum in Trends in E and E: max 1200 words?
Note in The American Naturalist: max 3000 words? Perspectives article in Nature?

\end{abstract}

\flushbottom
\maketitle
\newpage
\thispagestyle{empty}

\section*{Introduction}

For nearly a century statisticians and scientists have described the shortcomings of Null Hypothesis Significance Testing
(NHST) \citep[see][]{Cohen1994}. Research articles and books written in the past two decades proposing a deemphasis of the 
p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, 
Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}. Yet, both a reliance on NHST and the misinterpretation of 
results obtained from NHST remain high. In a 2017 meta-analysis of 356 studies published in \emph{European Sociological 
Research}, \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 
49\% interpreted non-significant effects as zero effects, and 44 \% failed to report an effect size in a comprehensible 
way. The misuse and misinterpretation of NHST is so pervasive that there has been a recent push for drastically reducing its 
use \citep{SzucsandIoannidis2017} or abandoning its use altogether \citep{McShaneetal.2017}. Others have called for a more
strenuous significance threshold (e.g. $p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce
the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold 
\citep{Ridleyetal.2007}

Alternatively, we suggest a change in the language used in NHST. Results from NHST (i.e. $p < or > 0.05$) should be 
described using language that directly corresponds to what a test of the null hypothesis actually tells us: whether or not 
we can \emph{clearly} see our effect. For example, given $H_{0} = 0$ (e.g. the difference in our treatments is 0) what a 
$p < 0.05$ tells us is whether or not we can clearly see the sign of the effect. Using the language of ``statistical 
clarity'' would help researchers escape the trap of accepting the null hypothesis and reduce multiple types of
misinterpretation associated with accepting the null hypothesis, while allowing for it to be retained as a method of 
inference (e.g. see \citealt{Abelson1997} for arguments for NHST). For example,equating $p < 0.05$ with a zero effect would 
be much harder to make once a researcher has written the following sentence: ``The difference between our control and 
treatment group was not statistically clear ($p = 0.24$). Additionally, the use of $p > 0.05$ as evidence for something 
(accepting the null hypothesis) would be more difficult if the following language was used: ``We were unable to clearly 
determine how our control and sham treatments differed''. Additionally, once ``significant'' regained its common English 
definition, conflating $p < 0.05$ with substantive significance would be more difficult.

\begin{itemize}
  \item Other topics to mention
  	\subitem difficulty in interpreting confidence intervals?
    \subitem usefulness of p --- use in splines: non-ridiculous standard to determine if we can see a pattern
    \subitem a p~value is not a property of reality (a biological ``thing''), but a property of a data set and assumptions...
\end{itemize}

\begin{itemize}
  \item To do
  	\subitem unsort bib for convenient lookup of types of cites
    \subitem links in bib to pdfs
\end{itemize}

\section*{Statistical Clarity}

\mk{Recount the way a high p is obtained?}

\subsection*{$\mathbf{p > 0.05 \neq}$ zero effect}

In the vast majority of scientific fields a truly zero, ``null effect'' does not exist \citep{Meehl1990, Tukey1991,
Cohen1994}. Yet, references to a null effect can still be found in high impact journals \citep[e.g.][]{Feldonetal.2017}. 
To emphasize that effects are not truly zero, descriptions of statistical results using the language of clarity should
begin with reference to the effect. For example, ``The difference between the control and treatment group was not 
statistically clear.''

\begin{itemize}
  \item Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Singhetal.2017}
\end{itemize}

\mk{Probably do not need this full description here}

Following a shift in language, we suggest using a non-inferiority test to test for a small effect. Consider the following 
example. A hospital is considering switching from bulky, expensive surgical face masks to lighter weight, cheaper masks. A
clinical trail that tests the effectiveness of both masks and finds $p > 0.05$ is not a success; this tells the hospital 
that the difference between the masks is not statistically clear! What the hospital actually want to know is whether the 
cheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}. This requires a $H_{0}$ that 
defines the target difference in effectiveness of the two masks that the hospital is willing to accept to make the 
transition. We note that this statistical test should be set up as a one-tailed test; the logical, \emph{a priori} 
assumption is that the bulky, expensive masks are more effective. In this case, a $p < 0.05$ tells the hospital that the 
difference between the new masks and old masks is small and that it they can proceed with the switch.

\begin{itemize}
  \item ``...establish the \emph{a priori} selection of an effect level that is considered unacceptably toxic:''
  \citep{Dentonetal.2011}
\end{itemize}

\subsection*{Using larger p~values as more evidence for something}

Another common mistake is using a larger p~value as stronger evidence for accepting the null hypothesis.  For example, 
\mk{Need a good quote here. An ok placeholder:} ``...yielded nonsignificant differences on measures of those skills with P 
values of at least 0.2, and most in the $0.7 \leq P \leq 0.9$ range.'' \citep{Feldonetal.2017}. A larger p value actually
corresponds to less clarity and thus the possibility of an undetected larger effect.

\mk{Point about focal vs non-focal hypotheses. Often accept the null for non-focal (diagnostics). While this is not
appropriate language it seems less bad...}

\begin{itemize}
  \item Setting out to accept the null: \citep{Karulinetal.2015}
\end{itemize}

\mk{Again, maybe this is too much}

Accepting the null is especially common in diagnostic tests. For example, a Shapiro-Wilk test of normality that
returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected
from a complicated world and does depart from normality). Without the goal of picking on any paper in specific, 
``...allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} 
is common language that should be avoided.

\subsection*{The difference between clear and not clear is not clear}

In 2006 Gelman and Stern wrote that the difference between statistically significant and statistically non-significant is
not itself significant. Rewritten using ``clarity'' this statement indicates that if a single result is not statistically 
clear, any comparison made between that unclear result and a clear result will not itself be a clear comparison. An example
taken from the literature is the following:

For example, if a treatment induces a statistically clear increase in growth rate in males, but has an unclear effect in 
females, the relationship between the treatment on males and females is not clear.

\begin{itemize}
  \item With the \emph{correlation coefficient} for males and females (but significance for only one sex---``substrate 
  choice correlated significantly with food choice in males'') the authors go on to describe biologically why the 
  correlation would be significant for males but not females. \citep{MerilaitaandJormalainen1997}
\end{itemize}

\subsection*{Conflating statistical and substantive significance}

In almost all cases what a researcher really cares about is the size of an effect and the scientific implications of the
effect. Statistical significance does not, in and of itself, tell us anything about substantive significance. As 
\citet{Bernardietal.2017} state, ``...sociological and social significance are sacrificed on the altar of statistical 
significance''. Included in this is an absence of reported effect sizes and confidence intervals.

\begin{itemize}
  \item Lack of clarity differentiating between biological and statistical significance: {Simonetal.2017}
  \item Complete lack of effect sizes: \citep{Juriadoetal.2017}
\end{itemize}

\section*{Closing Comments}

\begin{itemize}
  \item Topics we may want to bring up
	  \subitem Including a p~value helps to avoid type-S errors
\end{itemize}

Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016},
we conclude with a plea for an increased emphasis on effect sizes and confidence intervals. However, we suggest that the
use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing all ambiguity
from statements associated with $p < 0.05$. The statement ``The difference between our control and treatment groups were
statistically clear ($p = 0.007$)'' in unambiguously incomplete and uncompelling; an effect size and confidence interval 
is required to complete the story.

\mk{Not sure if we want any of this and how much we want to expand on any of these topics:}

We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, 
study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and 
reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low 
statistical power \citep[the "winners curse"][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}. 
Additionally, we are in favor of writing a statistical journal that chronicles all steps in the analysis process 
\citep{Kassetal.2016}, and clearly defining the boundary between results presented as inferences based on \emph{a priori}
hypotheses and those from \emph{post hoc} data exploration.

\subsection*{Acknowledgements}

We (probably will) thank the Bolker lab for helpful comments on the first draft of the manuscript.

### 2018-02-15 main.tex
Initial commit (copying roughly from failed overleaf)

\documentclass[12pt, english]{wlpeerj} % Just a convenient template
\usepackage{palatino}
\usepackage{subfiles}
\usepackage[english]{babel} 
\usepackage[comma]{natbib}
\bibliographystyle{chicago2}
\usepackage{url}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{float}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{tabularx}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage[colorlinks=true, citecolor = blue, linkcolor = black]{hyperref}
\usepackage{environ}
\usepackage{marginnote}
\usepackage{lineno}
\usepackage{setspace}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\reversemarginpar
\singlespacing

\newcommand{\jd}[1]{{\bf \color{blue} JD: #1}}
\newcommand{\mk}[1]{{\bf \color{red} MK: #1}}
\newcommand{\bmb}[1]{{\bf \color{green} BMB: #1}}

\title{Is statistical significance a thing?}

\author[1]{Jonathan Dushoff}
\author[1]{Morgan P. Kain}
\author[1,2]{Ben M. Bolker?}

\affil[1]{Department of Biology, McMaster University, 1280 Main Street West, Hamilton, Ontario L8S 4K1 Canada}
\affil[2]{Department of Mathematics and Statistics, McMaster University, 1280 Main Street West, Hamilton, Ontario 
L8S 4L8 Canada}

\corrauthor[1]{Jonathan Dushoff}{dushoff@mcmaster.ca}

\begin{document}

\input{doc.tex}

\newpage
\singlespacing

\bibliography{stat_signif}

\end{document}

### 2018-02-16 doc.tex
Update doc.tex

@@
 
-\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) has led to recent 
-calls for abandoning its use. We argue that statistical hypothesis tests are useful, but are not, and should not be 
-referred to, as tests of significance. We propose that a sensible method to reduce misconceptions about p~values 
+\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) has resulted in
+calls to abandon its use. Alternatively, we argue that statistical hypothesis tests are useful, but are not, and should not
+be referred to, as tests of significance. We propose that a sensible method to reduce misconceptions about NHST and p~values 
 is to refer to the results of NHST (i.e. $p < or > 0.05$) using ``statistical clarity''. A test of the null hypothesis tells 
-us whether or not we can \emph{clearly} see our effect (e.g. whether a correlation is positive or negative, or if a response 
-in the treatment group is greater than the response in the control group). Specifically, we argue the use of ``statistical
-clarity'' will help researchers avoid accepting the null hypothesis and retrieve the English definition for ``significance'' 
-to shift focus back to substantive significance.
+us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
+negative, or if a response in the treatment group is greater than the response in the control group). Specifically, we argue 
+that the use of ``statistical clarity'' will help researchers avoid accepting the null hypothesis and reclaim the English 
+definition for ``significance'', allowing for a shift in focus to substantive significance.
 
@@
 strenuous significance threshold (e.g. $p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce
-the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold 
-\citep{Ridleyetal.2007}
+the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold \citep{Ridleyetal.2007}.
 
-Alternatively, we suggest a change in the language used in NHST. Results from NHST (i.e. $p < or > 0.05$) should be 
-described using language that directly corresponds to what a test of the null hypothesis actually tells us: whether or not 
-we can \emph{clearly} see our effect. For example, given $H_{0} = 0$ (e.g. the difference in our treatments is 0) what a 
-$p < 0.05$ tells us is whether or not we can clearly see the sign of the effect. Using the language of ``statistical 
-clarity'' would help researchers escape the trap of accepting the null hypothesis and reduce multiple types of
-misinterpretation associated with accepting the null hypothesis, while allowing for it to be retained as a method of 
-inference (e.g. see \citealt{Abelson1997} for arguments for NHST). For example,equating $p < 0.05$ with a zero effect would 
-be much harder to make once a researcher has written the following sentence: ``The difference between our control and 
-treatment group was not statistically clear ($p = 0.24$). Additionally, the use of $p > 0.05$ as evidence for something 
-(accepting the null hypothesis) would be more difficult if the following language was used: ``We were unable to clearly 
-determine how our control and sham treatments differed''. Additionally, once ``significant'' regained its common English 
-definition, conflating $p < 0.05$ with substantive significance would be more difficult.
-
-\begin{itemize}
-  \item Other topics to mention
-  	\subitem difficulty in interpreting confidence intervals?
-    \subitem usefulness of p --- use in splines: non-ridiculous standard to determine if we can see a pattern
-    \subitem a p~value is not a property of reality (a biological ``thing''), but a property of a data set and assumptions...
-\end{itemize}
-
-\begin{itemize}
-  \item To do
-  	\subitem unsort bib for convenient lookup of types of cites
-    \subitem links in bib to pdfs
-\end{itemize}
+Instead, we suggest that using the language of ``statistical clarity'' would help researchers escape the trap of accepting 
+the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for
+the continued use of NHST as a method of inference (e.g. see \citealt{Abelson1997} for arguments for NHST). What a test of the
+null hypothesis actually tells us is whether or not we can \emph{clearly} see our effect. For example, given $H_{0} = 0$ (e.g.
+the difference in our treatments is 0) what a $p < 0.05$ tells us is whether or not we can clearly see the sign of the effect. 
+Therefore, results from NHST (i.e. $p < or > 0.05$) should be described using ``statistical clarity'' instead of ``statistical 
+significance''. For example, equating $p < 0.05$ with a zero effect would be much harder to make once a researcher has written 
+the following sentence: ``The difference between our control and treatment group was not statistically clear ($p = 0.24$). 
+Additionally, the use of larger p~values as increased evidence for the null would be more difficult if the following language
+was used: ``We were unable to clearly determine how our control and sham treatments differed''. Finally, in almost all cases 
+what a researcher really cares about is the size of an effect and the scientific implications of the effect.  As 
+\citet{Bernardietal.2017} state, ``...sociological and social significance are sacrificed on the altar of statistical 
+significance''. If ``significant'' were to reclaim its common English definition, conflating $p < 0.05$ with substantive
+significance would occur less frequently.
 
@@
 
-\mk{Recount the way a high p is obtained?}
+\mk{Language here needs a lot of work. Both in terms of clarity (haha) (use of ``confidence'' may be a bit confusing) and 
+because I am not sure that everything I am saying here is 100\% correct. Also not sure if this is how this section should
+start. Finally, portions of this have already been said in the paragraphs above.}
 
-\subsection*{$\mathbf{p > 0.05 \neq}$ zero effect}
+A p~value is not a property of reality (e.g. a biological phenomena), but is a property of a data set and the statistical test
+used. A p~value must therefore be interpreted and reported as a measure that quantifies our confidence about what we can see
+clearly about reality given our data. A $p < 0.05$ tells us that we are confident in in our ability to clearly see the sign
+of our effect (at an $\alpha = 0.05$ cutoff). While a direct illustration of this clarity is shown with the confidence 
+interval associated with $p < 0.05$, which will not overlap 0 (\mk{In nearly all cases?}), a p~value is a useful tool to 
+quantify this clarity. A p~value does not tell us about the substantive (e.g. biological) importance of our finding. Because
+the p~value is a property of the data, and a true zero,``null effect'' does not exist in the vast majority of scientific 
+fields \citep{Meehl1990, Tukey1991, Cohen1994}, $p < 0.05$ can be obtained for a very small effect with a large enough 
+sample size. Yet, references to a ``null effect'' can still be found in high impact journals \citep[e.g.][]{Feldonetal.2017}. 
+To emphasize that effects are not truly zero, descriptions of statistical results using the language of clarity should begin 
+with reference to the effect. For example, ``The difference between the control and treatment group was not statistically 
+clear.'' In Table~1 we provide examples from the literature of language that misinterprets p~values and a sensible way of
+rewriting these statements to reduce confusion.
 
-In the vast majority of scientific fields a truly zero, ``null effect'' does not exist \citep{Meehl1990, Tukey1991,
-Cohen1994}. Yet, references to a null effect can still be found in high impact journals \citep[e.g.][]{Feldonetal.2017}. 
-To emphasize that effects are not truly zero, descriptions of statistical results using the language of clarity should
-begin with reference to the effect. For example, ``The difference between the control and treatment group was not 
-statistically clear.''
+Another common mistake is using a larger p~value as stronger evidence for accepting the null hypothesis. A larger p value 
+actually corresponds to less clarity and thus the possibility of an undetected larger effect (see Table~1 for an example). In 
+2006 Gelman and Stern wrote that the difference between statistically significant and statistically non-significant is not 
+itself significant. Rewritten using ``clarity'' this statement indicates that if a single result is not statistically 
+clear, any comparison made between that unclear result and a clear result will not itself be a clear comparison. An example
+taken from the literature is in Table~1.
 
-\begin{itemize}
-  \item Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Singhetal.2017}
-\end{itemize}
+\mk{My table formatting skills are pretty bad}
 
-\mk{Probably do not need this full description here}
+\begin{framed}
+\begin{tabular}{p{7.5cm}p{7.5cm}}
+     Language in published journal articles & Rewritten using the language of ``clarity'' \\
+     	\hline
+        \\
+     \multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
+     	No relationship between individual genetic diversity and prevalence of avian malaria... & 
+        The relationship between individual genetic diversity and prevalence of avian malaria was not
+        statistically clear \\
+        \\
+     \multicolumn{2}{c}{\textbf{Using larger p~values as more evidence for something}} \\
+        ...yielded nonsignificant differences on measures of those skills with P values of 
+        at least 0.2, and most in the $0.7 \leq P \leq 0.9$ range. & 
+        ...the differences between skills developed in treatment and control individuals
+        were bot statistically clear ($p > 0.05$) \\
+        \\
+     \multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}} \\
+        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ 
+        but not in females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why
+        there is a relationship between these variables in males, but not in females & 
+        Substrate choice was positively correlated with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$,
+        but this relationship was not statistically clear in females $(r_{s} = 0.32, N = 24, NS)$. A biological
+        description comparing the correlation in males vs females is inappropriate without a direct test (in
+        this case with the exact same correlation estimate, this is not a sensible test). \\
+\end{tabular}
+\end{framed}
+   \captionof{table}{Rewriting misinformed language in the published literature using our proposed updated language.}
+
+\section*{Closing Comments}
+
+\subsection*{Non-inferiority tests}
 
@@
 
-\begin{itemize}
-  \item ``...establish the \emph{a priori} selection of an effect level that is considered unacceptably toxic:''
-  \citep{Dentonetal.2011}
-\end{itemize}
-
-\subsection*{Using larger p~values as more evidence for something}
-
-Another common mistake is using a larger p~value as stronger evidence for accepting the null hypothesis.  For example, 
-\mk{Need a good quote here. An ok placeholder:} ``...yielded nonsignificant differences on measures of those skills with P 
-values of at least 0.2, and most in the $0.7 \leq P \leq 0.9$ range.'' \citep{Feldonetal.2017}. A larger p value actually
-corresponds to less clarity and thus the possibility of an undetected larger effect.
-
-\mk{Point about focal vs non-focal hypotheses. Often accept the null for non-focal (diagnostics). While this is not
-appropriate language it seems less bad...}
-
-\begin{itemize}
-  \item Setting out to accept the null: \citep{Karulinetal.2015}
-\end{itemize}
-
-\mk{Again, maybe this is too much}
+\subsection*{Focal vs non-focal hypotheses}
 
@@
 
-\subsection*{The difference between clear and not clear is not clear}
-
-In 2006 Gelman and Stern wrote that the difference between statistically significant and statistically non-significant is
-not itself significant. Rewritten using ``clarity'' this statement indicates that if a single result is not statistically 
-clear, any comparison made between that unclear result and a clear result will not itself be a clear comparison. An example
-taken from the literature is the following:
-
-For example, if a treatment induces a statistically clear increase in growth rate in males, but has an unclear effect in 
-females, the relationship between the treatment on males and females is not clear.
-
-\begin{itemize}
-  \item With the \emph{correlation coefficient} for males and females (but significance for only one sex---``substrate 
-  choice correlated significantly with food choice in males'') the authors go on to describe biologically why the 
-  correlation would be significant for males but not females. \citep{MerilaitaandJormalainen1997}
-\end{itemize}
-
-\subsection*{Conflating statistical and substantive significance}
-
-In almost all cases what a researcher really cares about is the size of an effect and the scientific implications of the
-effect. Statistical significance does not, in and of itself, tell us anything about substantive significance. As 
-\citet{Bernardietal.2017} state, ``...sociological and social significance are sacrificed on the altar of statistical 
-significance''. Included in this is an absence of reported effect sizes and confidence intervals.
-
-\begin{itemize}
-  \item Lack of clarity differentiating between biological and statistical significance: {Simonetal.2017}
-  \item Complete lack of effect sizes: \citep{Juriadoetal.2017}
-\end{itemize}
-
-\section*{Closing Comments}
-
-\begin{itemize}
-  \item Topics we may want to bring up
-	  \subitem Including a p~value helps to avoid type-S errors
-\end{itemize}
+\subsection*{Previous suggestions}
 
@@
 is required to complete the story.
-
-\mk{Not sure if we want any of this and how much we want to expand on any of these topics:}
 
@@
 
+\section*{Lists}
+
+\begin{itemize}
+  \item Topics we may want to bring up
+	  \subitem Including a p~value helps to avoid type-S errors
+      \subitem usefulness of p --- use in splines: non-ridiculous standard to determine if we can see a pattern
+      \subitem difficulty in interpreting confidence intervals?
+\end{itemize}
+
+\begin{itemize}
+  \item Examples
+  \subitem Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Singhetal.2017}
+  \subitem Lack of clarity differentiating between biological and statistical significance: {Simonetal.2017}
+  \subitem Complete lack of effect sizes: \citep{Juriadoetal.2017}
+  \subitem Setting out to accept the null: \citep{Karulinetal.2015}
+  \subitem ``...establish the \emph{a priori} selection of an effect level that is considered unacceptably toxic:'' \citep{Dentonetal.2011}
+  \subitem With the \emph{correlation coefficient} for males and females (but significance for only one sex---``substrate 
+  choice correlated significantly with food choice in males'') the authors go on to describe biologically why the 
+  correlation would be significant for males but not females. \citep{MerilaitaandJormalainen1997}
+\end{itemize}
+
+\begin{itemize}
+  \item To do
+  	\subitem unsort bib for convenient lookup of types of cites
+    \subitem links in bib to pdfs
+\end{itemize}
+
 \subsection*{Acknowledgements}
 
-We (probably will) thank the Bolker lab for helpful comments on the first draft of the manuscript.
+We thank members of the Dushoff and Bolker labs for helpful comments on the first draft of the manuscript.

### 2018-02-26 doc.tex
Update doc.tex

@@
 \begin{abstract}
-
-\mk{Unedited placeholder text}
 
@@
      \multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
-     	No relationship between individual genetic diversity and prevalence of avian malaria... & 
-        The relationship between individual genetic diversity and prevalence of avian malaria was not
-        statistically clear \\
+        Cadmium bioaccumulates after acute exposure but has no effect on locomotion or shelter-seeking behaviour in the
+        invasive green shore crab & Cadmium bioaccumulates after acute exposure but its effect on locomotion or shelter-seeking 
+        behaviour in the invasive green shore crab was statistically unclear \\ 
         \\
-     \multicolumn{2}{c}{\textbf{Using larger p~values as more evidence for something}} \\
-        ...yielded nonsignificant differences on measures of those skills with P values of 
-        at least 0.2, and most in the $0.7 \leq P \leq 0.9$ range. & 
-        ...the differences between skills developed in treatment and control individuals
-        were bot statistically clear ($p > 0.05$) \\
+        No effect of elevated carbon dioxide on reproductive behaviors in the three-spined stickleback & The effect of elevated 
+        carbon dioxide on reproductive behaviors in the three-spined stickleback was statistically unclear \\
+        \\
+        The finding that bee species richness showed no significant relationship with the area of semi-natural habitat is 
+        surprising because bee species richness is usually more strongly influenced by landscape context than pollination. & 
+        Bee species richness is often found to be more strongly influenced by landscape context than pollination; however, 
+        in the present study the relationship between bee species richness and area of semi-natural habitat was statistically 
+        unclear \\ 
+        \\
+     \multicolumn{2}{c}{\textbf{P~values $\mathbf{> 0.05}$ should not be compared as evidence for anything}} \\
+        ...yielded nonsignificant differences on measures of those skills with P values of at least 0.2, and most in the
+        $0.7 \leq P \leq 0.9$ range. & ...the differences between skills developed in treatment and control individuals
+        were not statistically clear ($p > 0.05$) \\
         \\
      \multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}} \\
-        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ 
-        but not in females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why
-        there is a relationship between these variables in males, but not in females & 
-        Substrate choice was positively correlated with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$,
-        but this relationship was not statistically clear in females $(r_{s} = 0.32, N = 24, NS)$. A biological
-        description comparing the correlation in males vs females is inappropriate without a direct test (in
-        this case with the exact same correlation estimate, this is not a sensible test). \\
+        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ but not in
+        females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why there is a relationship 
+        between these variables in males, but not in females & Substrate choice was positively correlated with food choice in 
+        males $(r_{s} = 0.32, N = 44, P < 0.05)$, but this relationship was not statistically clear in females $(r_{s} = 0.32,
+        N = 24, NS)$. A biological description comparing the correlation in males vs females is inappropriate without a direct
+        test (in this case with the exact same correlation estimate, this is not a sensible test). \\
 \end{tabular}
@@
   \item Examples
-  \subitem Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Singhetal.2017}
+  \subitem Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Bukovinszkyetal.2017, Singhetal.2017, Sundinetal.2017}
   \subitem Lack of clarity differentiating between biological and statistical significance: {Simonetal.2017}

### 2018-02-28 doc.tex
Update doc.tex

@@
 
-\begin{framed}
 \begin{tabular}{p{7.5cm}p{7.5cm}}
@@
         females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why there is a relationship 
-        between these variables in males, but not in females & Substrate choice was positively correlated with food choice in 
-        males $(r_{s} = 0.32, N = 44, P < 0.05)$, but this relationship was not statistically clear in females $(r_{s} = 0.32,
-        N = 24, NS)$. A biological description comparing the correlation in males vs females is inappropriate without a direct
-        test (in this case with the exact same correlation estimate, this is not a sensible test). \\
+        between these variables in males, but not in females & 
+        Substrate choice was positively correlated with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$, but this
+        relationship was not statistically clear in females $(r_{s} = 0.32, N = 24, NS)$. A biological description comparing 
+        the correlation in males vs females is inappropriate without a direct test (in this case with the exact same 
+        correlation estimate, this is not a sensible test). \\
+        \\
+        ...risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
+        (adjusted OR 2.99, 95\% CI 1.33–6.74), but no association was found between HCV coinfection and low BMD in men 
+        (adjusted OR 1.26, 95\% CI 0.75–2.10). ... While the authors do not directly compare men and women they do state: 
+        The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men 
+        remain unclear. & 
+        ..risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
+        (adjusted OR 2.99, 95\% CI 1.33–6.74), but the association between HCV coinfection and low BMD in men was not
+        statistically clear (adjusted OR 1.26, 95\% CI 0.75–2.10). ... Pursuing the biological importance of HIV on BMD in 
+        women and not men is premature given these statistics and requires further study.
+        \\
 \end{tabular}
-\end{framed}
    \captionof{table}{Rewriting misinformed language in the published literature using our proposed updated language.}

### 2018-04-05 doc.tex
add refs to bib; oikos note

@@
 Note in The American Naturalist: max 3000 words? Perspectives article in Nature?
+Oikos forum?
+\url{http://www.oikosjournal.org/authors/author-guidelines}: ``Proposals should be no more than half a page in length and should include statements about the novelty and need for the piece as well as suggestions with regard to which members of the editorial board would be most suited to evaluating the proposal.''
 

### 2018-04-05 doc.tex
a few tweaks

@@
 
-\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) has resulted in
+\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) have resulted in
 calls to abandon its use. Alternatively, we argue that statistical hypothesis tests are useful, but are not, and should not
-be referred to, as tests of significance. We propose that a sensible method to reduce misconceptions about NHST and p~values 
-is to refer to the results of NHST (i.e. $p < or > 0.05$) using ``statistical clarity''. A test of the null hypothesis tells 
+be referred to, as tests of significance. We propose a simple method to reduce misconceptions about NHST and p~values: 
+refer to the results of NHST (i.e. $p <$ or $> 0.05$) using ``statistical clarity'' rather than ``statistical significance''. A test of the null hypothesis tells 
 us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
@@
 we conclude with a plea for an increased emphasis on effect sizes and confidence intervals. However, we suggest that the
-use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing all ambiguity
-from statements associated with $p < 0.05$. The statement ``The difference between our control and treatment groups were
-statistically clear ($p = 0.007$)'' in unambiguously incomplete and uncompelling; an effect size and confidence interval 
+use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing ambiguity
+from statements associated with $p < 0.05$. The statement ``The difference between our control and treatment groups was
+statistically clear ($p = 0.007$)'' is unambiguously incomplete; an effect size and confidence interval 
 is required to complete the story.

### 2018-05-04 doc.tex
Meeting with BB
Interrupted (working with BB earlier)

@@
 
-\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) have resulted in
-calls to abandon its use. Alternatively, we argue that statistical hypothesis tests are useful, but are not, and should not
+\textbf{Abstract}: Null hypothesis significance testing (NHST) remains popular despite decades of concern about misuse and misinterpretation.
+Here we argue that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word commonly uis not about  whatever the use of have led to debates over whether to abandon its use.
+What to say about when and how they are useful? 
+Conflation?
+Get to the point!
+Part of the problem here is the use of the word ``significance''. 
+While hypothesis testing may be Here, we argue that statistical hypothesis tests are useful, but are not, and should not
 be referred to, as tests of significance. We propose a simple method to reduce misconceptions about NHST and p~values: 
-refer to the results of NHST (i.e. $p <$ or $> 0.05$) using ``statistical clarity'' rather than ``statistical significance''. A test of the null hypothesis tells 
+refer to the results of NHST (e.g. $p <$ or $> 0.05$) using ``statistical clarity'' rather than ``statistical significance''. 
+A test of the null hypothesis tells 
 us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
@@
 
-\textbf{Venue:} \mk{My list, no input from PIs on this yet}. No idea... Forum in Trends in E and E: max 1200 words?
+\textbf{Venue:} Forum in Trends in E and E: max 1200 words?
 Note in The American Naturalist: max 3000 words? Perspectives article in Nature?

### 2018-05-15 doc.tex
Slight progress (for lots of effort)

--- 2018-04-05 doc.tex
@@
 
-\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) have resulted in
-calls to abandon its use. Alternatively, we argue that statistical hypothesis tests are useful, but are not, and should not
-be referred to, as tests of significance. We propose a simple method to reduce misconceptions about NHST and p~values: 
-refer to the results of NHST (i.e. $p <$ or $> 0.05$) using ``statistical clarity'' rather than ``statistical significance''. A test of the null hypothesis tells 
-us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
-negative, or if a response in the treatment group is greater than the response in the control group). Specifically, we argue 
-that the use of ``statistical clarity'' will help researchers avoid accepting the null hypothesis and reclaim the English 
-definition for ``significance'', allowing for a shift in focus to substantive significance.
+\textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
+We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
+commonly uis not about  whatever the use of have led to debates over whether to abandon its use.
+Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
+whether we can clearly see that a correlation or between-group difference is positive or negative).
+We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
+We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.
+
+\end{abstract}
+
+\flushbottom
+\maketitle
+\newpage
+\thispagestyle{empty}
+
+\section*{Notes}
 
@@
 
+\textbf{Signs}. Who has said before that we test zero \emph{because} we want to know if we can see a sign clearly? If nobody, how much time do we want to spend on that point?
+
 \textbf{Notes:} A lot of this language assumes $H_{0} = 0$. Probably need to address clearly that many of these cited
@@
 
-\end{abstract}
-
-\flushbottom
-\maketitle
-\newpage
-\thispagestyle{empty}
+\clearpage
 
@@
 p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, 
-Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}. Yet, both a reliance on NHST and the misinterpretation of 
+Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}. Yet, both reliance on NHST and the misinterpretation of 
 results obtained from NHST remain high. In a 2017 meta-analysis of 356 studies published in \emph{European Sociological 
 Research}, \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 
-49\% interpreted non-significant effects as zero effects, and 44 \% failed to report an effect size in a comprehensible 
+49\% interpreted non-significant effects as zero effects, and 44\% failed to report an effect size in a comprehensible 
 way. The misuse and misinterpretation of NHST is so pervasive that there has been a recent push for drastically reducing its 
@@
 the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for
-the continued use of NHST as a method of inference (e.g. see \citealt{Abelson1997} for arguments for NHST). What a test of the
+the continued use of NHST as a method of inference (e.g. see \citealt{Abelson1997} for arguments for NHST).
+
+As an example, consider \jd{Should I write a paragraph about signs and clarity?}
+The argument for clarity is clearest in the case of What a test of the
 null hypothesis actually tells us is whether or not we can \emph{clearly} see our effect. For example, given $H_{0} = 0$ (e.g.
 the difference in our treatments is 0) what a $p < 0.05$ tells us is whether or not we can clearly see the sign of the effect.
+
 Therefore, results from NHST (i.e. $p < or > 0.05$) should be described using ``statistical clarity'' instead of ``statistical 

### 2018-05-15 doc.tex
two small comments in the abstract

@@
 \textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
-We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
-commonly uis not about  whatever the use of have led to debates over whether to abandon its use.
+We believe that a significant \mk{change word?} part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
+\mk{Broken sentence:} commonly uis not about  whatever the use of have led to debates over whether to abandon its use.
 Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.

### 2018-05-16 doc.tex
Re-drafted intro

--- 2018-05-15 doc.tex
@@
 \textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
-We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
-commonly uis not about  whatever the use of have led to debates over whether to abandon its use.
+We believe that a significant \mk{change word?}\jd{I did this on purpose (and also end with ``clarity'').
+Too cute?
+I kind of think it could help make the point.} part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
+
 Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
@@
 \textbf{Structure:} I like the idea of two parallel boxes that have examples of language used in published papers on the
-left and corrected language on the right. Maybe three examples that correspond to four primary misinterpretations people
+left and corrected language on the right.
+Maybe three examples that correspond to four primary misinterpretations people
 make (zero effect, large p-values as ``more'' evidence for something, difference between clear and not clear is not clear,
@@
 p-values, though the idea of changing the language to clarity and retrieving the English definition of significant
-is novel. \citet{Bernardietal.2017} and \citet{McShaneetal.2017} have covered a lot of the history that is
-recounted below. It may be best to just cite these papers and state that concern about NHST and p-value abuse 
-remains high. \citep{Bernardietal.2017} present an analysis of the presence of errors in the interpretation of 
+is novel.
+\citet{Bernardietal.2017} and \citet{McShaneetal.2017} have covered a lot of the history that is
+recounted below.
+It may be best to just cite these papers and state that concern about NHST and p-value abuse 
+remains high.
+\citep{Bernardietal.2017} present an analysis of the presence of errors in the interpretation of 
 results and ambiguity in language focused on NHST. Out of  They point out that these results are similar to the
@@
 
-\textbf{Signs}. Who has said before that we test zero \emph{because} we want to know if we can see a sign clearly? If nobody, how much time do we want to spend on that point?
+\textbf{Signs}.
+Who has said before that we test zero \emph{because} we want to know if we can see a sign clearly? If nobody, how much time do we want to spend on that point?
 
 \textbf{Notes:} A lot of this language assumes $H_{0} = 0$. Probably need to address clearly that many of these cited
-papers are based in psychology. I imagine we will want to anonymize quotes? (Though I kind of want to call out the null
+papers are based in psychology.
+I imagine we will want to anonymize quotes? (Though I kind of want to call out the null
 result short courses paper --- maybe as a point about non-significance and calling for reform)
@@
 
-For nearly a century statisticians and scientists have described the shortcomings of Null Hypothesis Significance Testing
-(NHST) \citep[see][]{Cohen1994}. Research articles and books written in the past two decades proposing a deemphasis of the 
-p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, 
-Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}. Yet, both reliance on NHST and the misinterpretation of 
-results obtained from NHST remain high. In a 2017 meta-analysis of 356 studies published in \emph{European Sociological 
-Research}, \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 
+For nearly a century statisticians and scientists have described the shortcomings of Null Hypothesis Significance Testing (NHST) \citep[see][]{Cohen1994}.
+
+Books and articles proposing a deemphasis of the p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
+
+Yet, both reliance on NHST and the misinterpretation of results obtained from NHST remain high.
+
+In a 2017 meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 
 49\% interpreted non-significant effects as zero effects, and 44\% failed to report an effect size in a comprehensible 
-way. The misuse and misinterpretation of NHST is so pervasive that there has been a recent push for drastically reducing its 
-use \citep{SzucsandIoannidis2017} or abandoning its use altogether \citep{McShaneetal.2017}. Others have called for a more
-strenuous significance threshold (e.g. $p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce
+way.
+The misuse and misinterpretation of NHST is so pervasive that there has been a recent push for drastically reducing 
+\citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
+
+Others have called for a more
+strenuous significance threshold (e.g.
+$p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce
 the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold \citep{Ridleyetal.2007}.
@@
 the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for
-the continued use of NHST as a method of inference (e.g. see \citealt{Abelson1997} for arguments for NHST).
+the continued use of NHST as a method of inference (e.g.
+see \citealt{Abelson1997} for arguments for NHST).
+``Clarity'' is a particularly apt term for what hypothesis tests evaluate.
+A strong argument in favor or NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true)  is a proxy for asking whether we can see a difference clearly.
+In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \cite{robinson2001past}.
 
-As an example, consider \jd{Should I write a paragraph about signs and clarity?}
-The argument for clarity is clearest in the case of What a test of the
-null hypothesis actually tells us is whether or not we can \emph{clearly} see our effect. For example, given $H_{0} = 0$ (e.g.
-the difference in our treatments is 0) what a $p < 0.05$ tells us is whether or not we can clearly see the sign of the effect.
-
-Therefore, results from NHST (i.e. $p < or > 0.05$) should be described using ``statistical clarity'' instead of ``statistical 
-significance''. For example, equating $p < 0.05$ with a zero effect would be much harder to make once a researcher has written 
-the following sentence: ``The difference between our control and treatment group was not statistically clear ($p = 0.24$). 
-Additionally, the use of larger p~values as increased evidence for the null would be more difficult if the following language
-was used: ``We were unable to clearly determine how our control and sham treatments differed''. Finally, in almost all cases 
-what a researcher really cares about is the size of an effect and the scientific implications of the effect.  As 
-\citet{Bernardietal.2017} state, ``...sociological and social significance are sacrificed on the altar of statistical 
-significance''. If ``significant'' were to reclaim its common English definition, conflating $p < 0.05$ with substantive
-significance would occur less frequently.
+Using this language could make sloppy communication and sloppy thinking more difficult. 
+For example, we often see sentences like, ``X et al. showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
+In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about their study, not about the underlying processes \cite{CanWeCiteThis}.
+A better formulation would be ``X et al. did not find a significant effect of Y on Z.''
+It seems likely, however, that this mistake would be harder to make using the language of clarity:  ``X et al. showed that the effect of Y on Z is unclear'' seems awkward.
+Similarly, ``We did not find a clear difference in response between the control and sham groups'' seems both more colloquially accurate and harder to transform into something misleading than ``We did not find a significant difference\ldots''.
+\citet{Bernardietal.2017} argued that ``...sociological and social significance are sacrificed on the altar of statistical significance''.
+Describing statistical tests in terms of clarity could allow ``significant'' to reclaim its common English definition, and reduce conflation between statistical results and substantive significance.
 
@@
 
-\mk{Language here needs a lot of work. Both in terms of clarity (haha) (use of ``confidence'' may be a bit confusing) and 
-because I am not sure that everything I am saying here is 100\% correct. Also not sure if this is how this section should
-start. Finally, portions of this have already been said in the paragraphs above.}
+\mk{Language here needs a lot of work.
+Both in terms of clarity (haha) (use of ``confidence'' may be a bit confusing) and 
+because I am not sure that everything I am saying here is 100\% correct.
+Also not sure if this is how this section should
+start.
+Finally, portions of this have already been said in the paragraphs above.}
 
-A p~value is not a property of reality (e.g. a biological phenomena), but is a property of a data set and the statistical test
-used. A p~value must therefore be interpreted and reported as a measure that quantifies our confidence about what we can see
-clearly about reality given our data. A $p < 0.05$ tells us that we are confident in in our ability to clearly see the sign
-of our effect (at an $\alpha = 0.05$ cutoff). While a direct illustration of this clarity is shown with the confidence 
+A p~value is not a property of reality (e.g.
+a biological phenomena), but is a property of a data set and the statistical test
+used.
+A p~value must therefore be interpreted and reported as a measure that quantifies our confidence about what we can see
+clearly about reality given our data.
+A $p < 0.05$ tells us that we are confident in in our ability to clearly see the sign
+of our effect (at an $\alpha = 0.05$ cutoff).
+While a direct illustration of this clarity is shown with the confidence 
 interval associated with $p < 0.05$, which will not overlap 0 (\mk{In nearly all cases?}), a p~value is a useful tool to 
-quantify this clarity. A p~value does not tell us about the substantive (e.g. biological) importance of our finding. Because
+quantify this clarity.
+A p~value does not tell us about the substantive (e.g.
+biological) importance of our finding.
+Because
 the p~value is a property of the data, and a true zero,``null effect'' does not exist in the vast majority of scientific 
 fields \citep{Meehl1990, Tukey1991, Cohen1994}, $p < 0.05$ can be obtained for a very small effect with a large enough 
-sample size. Yet, references to a ``null effect'' can still be found in high impact journals \citep[e.g.][]{Feldonetal.2017}. 
+sample size.
+Yet, references to a ``null effect'' can still be found in high impact journals \citep[e.g.][]{Feldonetal.2017}. 
 To emphasize that effects are not truly zero, descriptions of statistical results using the language of clarity should begin 
-with reference to the effect. For example, ``The difference between the control and treatment group was not statistically 
+with reference to the effect.
+For example, ``The difference between the control and treatment group was not statistically 
 clear.'' In Table~1 we provide examples from the literature of language that misinterprets p~values and a sensible way of
@@
 
-Another common mistake is using a larger p~value as stronger evidence for accepting the null hypothesis. A larger p value 
-actually corresponds to less clarity and thus the possibility of an undetected larger effect (see Table~1 for an example). In 
+Another common mistake is using a larger p~value as stronger evidence for accepting the null hypothesis.
+A larger p value 
+actually corresponds to less clarity and thus the possibility of an undetected larger effect (see Table~1 for an example).
+In 
 2006 Gelman and Stern wrote that the difference between statistically significant and statistically non-significant is not 
-itself significant. Rewritten using ``clarity'' this statement indicates that if a single result is not statistically 
-clear, any comparison made between that unclear result and a clear result will not itself be a clear comparison. An example
+itself significant.
+Rewritten using ``clarity'' this statement indicates that if a single result is not statistically 
+clear, any comparison made between that unclear result and a clear result will not itself be a clear comparison.
+An example
 taken from the literature is in Table~1.
@@
         The finding that bee species richness showed no significant relationship with the area of semi-natural habitat is 
-        surprising because bee species richness is usually more strongly influenced by landscape context than pollination. & 
+        surprising because bee species richness is usually more strongly influenced by landscape context than pollination.
+& 
         Bee species richness is often found to be more strongly influenced by landscape context than pollination; however, 
@@
         ...yielded nonsignificant differences on measures of those skills with P values of at least 0.2, and most in the
-        $0.7 \leq P \leq 0.9$ range. & ...the differences between skills developed in treatment and control individuals
+        $0.7 \leq P \leq 0.9$ range.
+& ...the differences between skills developed in treatment and control individuals
         were not statistically clear ($p > 0.05$) \\
@@
         the correlation in males vs females is inappropriate without a direct test (in this case with the exact same 
-        correlation estimate, this is not a sensible test). \\
+        correlation estimate, this is not a sensible test).
+\\
         \\
@@
         The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men 
-        remain unclear. & 
+        remain unclear.
+& 
         ..risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
@@
 
-Following a shift in language, we suggest using a non-inferiority test to test for a small effect. Consider the following 
-example. A hospital is considering switching from bulky, expensive surgical face masks to lighter weight, cheaper masks. A
+Following a shift in language, we suggest using a non-inferiority test to test for a small effect.
+Consider the following 
+example.
+A hospital is considering switching from bulky, expensive surgical face masks to lighter weight, cheaper masks.
+A
 clinical trail that tests the effectiveness of both masks and finds $p > 0.05$ is not a success; this tells the hospital 
 that the difference between the masks is not statistically clear! What the hospital actually want to know is whether the 
-cheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}. This requires a $H_{0}$ that 
+cheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}.
+This requires a $H_{0}$ that 
 defines the target difference in effectiveness of the two masks that the hospital is willing to accept to make the 
-transition. We note that this statistical test should be set up as a one-tailed test; the logical, \emph{a priori} 
-assumption is that the bulky, expensive masks are more effective. In this case, a $p < 0.05$ tells the hospital that the 
+transition.
+We note that this statistical test should be set up as a one-tailed test; the logical, \emph{a priori} 
+assumption is that the bulky, expensive masks are more effective.
+In this case, a $p < 0.05$ tells the hospital that the 
 difference between the new masks and old masks is small and that it they can proceed with the switch.
@@
 
-Accepting the null is especially common in diagnostic tests. For example, a Shapiro-Wilk test of normality that
+Accepting the null is especially common in diagnostic tests.
+For example, a Shapiro-Wilk test of normality that
 returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected
-from a complicated world and does depart from normality). Without the goal of picking on any paper in specific, 
+from a complicated world and does depart from normality).
+Without the goal of picking on any paper in specific, 
 ``...allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} 
@@
 Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016},
-we conclude with a plea for an increased emphasis on effect sizes and confidence intervals. However, we suggest that the
+we conclude with a plea for an increased emphasis on effect sizes and confidence intervals.
+However, we suggest that the
 use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing ambiguity
@@
   choice correlated significantly with food choice in males'') the authors go on to describe biologically why the 
-  correlation would be significant for males but not females. \citep{MerilaitaandJormalainen1997}
+  correlation would be significant for males but not females.
+\citep{MerilaitaandJormalainen1997}
 \end{itemize}

### 2018-05-25 doc.tex

@@
 Who has said before that we test zero \emph{because} we want to know if we can see a sign clearly? If nobody, how much time do we want to spend on that point? 
+From \citet{robinson2001past}, which arose from \citet{jones2000sensible}: [instead of no difference, or no statistical difference] "authors should instead simply state that `the direction of the differences among the treatments was undetermined' or that `the sign of the correlation among the two variables was undetermined.'" --- That is, "If p is greater than 0.05, the conclusion is simply that the sign of the difference is not yet determined"
 

### 2018-06-19 doc.tex
Some small edits.

@@
 Note in The American Naturalist: max 3000 words? Perspectives article in Nature?
-Oikos forum?
-\url{http://www.oikosjournal.org/authors/author-guidelines}: ``Proposals should be no more than half a page in length and should include statements about the novelty and need for the piece as well as suggestions with regard to which members of the editorial board would be most suited to evaluating the proposal.''
+Rejected by Oikos forum!
 
@@
 For nearly a century statisticians and scientists have described the shortcomings of Null Hypothesis Significance Testing (NHST) \citep[see][]{Cohen1994}.
-
 Books and articles proposing a deemphasis of the p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
-
 Yet, both reliance on NHST and the misinterpretation of results obtained from NHST remain high.
@@
 \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
-
 Others have called for a more
@@
 see \citealt{Abelson1997} for arguments for NHST).
-``Clarity'' is a particularly apt term for what hypothesis tests evaluate.
-A strong argument in favor or NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true)  is a proxy for asking whether we can see a difference clearly.
+The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the P value is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
+``Clarity,'' on the other hand, is a particularly apt term for what hypothesis tests evaluate: a strong argument in favor or NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
 In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \cite{robinson2001past}.
 
-Using this language could make sloppy communication and sloppy thinking more difficult. 
+Using the language of clarity makes sloppy thinking and misleading communication more difficult. 
 For example, we often see sentences like, ``X et al. showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).

### 2018-06-20 doc.tex
In the middle of reworking (and anonymizing) the table

@@
 The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the P value is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
-``Clarity,'' on the other hand, is a particularly apt term for what hypothesis tests evaluate: a strong argument in favor or NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
+``Clarity,'' on the other hand, is an apt term for what hypothesis tests evaluate: a strong argument in favor of NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
 In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \cite{robinson2001past}.
@@
 A better formulation would be ``X et al. did not find a significant effect of Y on Z.''
-It seems likely, however, that this mistake would be harder to make using the language of clarity:  ``X et al. showed that the effect of Y on Z is unclear'' seems awkward.
+This mistake seems harder to make using the language of clarity:  ``X et al. showed that the effect of Y on Z is unclear'' is awkward.
 Similarly, ``We did not find a clear difference in response between the control and sham groups'' seems both more colloquially accurate and harder to transform into something misleading than ``We did not find a significant difference\ldots''.
@@
 
-A p~value is not a property of reality (e.g.
-a biological phenomena), but is a property of a data set and the statistical test
-used.
-A p~value must therefore be interpreted and reported as a measure that quantifies our confidence about what we can see
-clearly about reality given our data.
+A p~value is not a property of reality (e.g.  a biological phenomena), but is a property of a data set and the statistical test used.
+A p~value must therefore be interpreted and reported as a measure that quantifies our confidence about what we can see clearly about reality given our data.
 A $p < 0.05$ tells us that we are confident in in our ability to clearly see the sign
@@
 
-\begin{tabular}{p{7.5cm}p{7.5cm}}
-     Language in published journal articles & Rewritten using the language of ``clarity'' \\
-     	\hline
+\setlength\tabcolsep{1cm}.
+\begin{tabular}{p{7.0cm}p{7.0cm}}
+Language from published articles & Rewritten using ``clarity'' \\
+\hline\\
+
+\multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
+
+Toxins accumulate after acute exposure but have no effect on behaviour
+& Toxins accumulate after acute exposure but effects on behaviour are statistically unclear
 \\
-     \multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
-        Cadmium bioaccumulates after acute exposure but has no effect on locomotion or shelter-seeking behaviour in the
-        invasive green shore crab & Cadmium bioaccumulates after acute exposure but its effect on locomotion or shelter-seeking 
-        behaviour in the invasive green shore crab was statistically unclear \\ 
+
+There was no effect of elevated carbon dioxide on reproductive behaviors 
+& The effect of elevated carbon dioxide on reproductive behaviors was statistically unclear
 \\
-        No effect of elevated carbon dioxide on reproductive behaviors in the three-spined stickleback & The effect of elevated 
-        carbon dioxide on reproductive behaviors in the three-spined stickleback was statistically unclear \\
+
+The finding that species richness showed no significant relationship with the area of available habitat is surprising because richness is usually strongly influenced by landscape context 
+& Although species richness is usually strongly influenced by landscape context, in the present study this relationship was not statistically clear 
+\\ \\
+
+\multicolumn{2}{c}{\textbf{Comparing P~values}}
 \\
-        The finding that bee species richness showed no significant relationship with the area of semi-natural habitat is 
-        surprising because bee species richness is usually more strongly influenced by landscape context than pollination.
-& 
-        Bee species richness is often found to be more strongly influenced by landscape context than pollination; however, 
-        in the present study the relationship between bee species richness and area of semi-natural habitat was statistically 
-        unclear \\ 
+
+\ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
+& \ldots\ differences between treatment and control groups were not statistically clear ($P > 0.05$)
+\\ \\
+
+\multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}}
 \\
-     \multicolumn{2}{c}{\textbf{P~values $\mathbf{> 0.05}$ should not be compared as evidence for anything}} \\
-        ...yielded nonsignificant differences on measures of those skills with P values of at least 0.2, and most in the
-        $0.7 \leq P \leq 0.9$ range.
-& ...the differences between skills developed in treatment and control individuals
-        were not statistically clear ($p > 0.05$) \\
+
+This correlation was significant in males ($\rho=0.35$, P \textless 0.05) but not females ($\rho=0.35$, NS).
+\ldots [Afterwards the assumption is that a difference between males and females has been demonstrated]
+& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots [This phrasing may suggest to the authors that confidence intervals are called for.]
 \\
-     \multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}} \\
-        Substrate choice correlated significantly with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$ but not in
-        females $(r_{s} = 0.32, N = 24, NS)$. ... The authors discuss the biological reasons why there is a relationship 
-        between these variables in males, but not in females & 
-        Substrate choice was positively correlated with food choice in males $(r_{s} = 0.32, N = 44, P < 0.05)$, but this
-        relationship was not statistically clear in females $(r_{s} = 0.32, N = 24, NS)$. A biological description comparing 
-        the correlation in males vs females is inappropriate without a direct test (in this case with the exact same 
-        correlation estimate, this is not a sensible test).
-\\
-        \\
+
 ...risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone

### 2018-08-03 doc.tex
Update doc.tex

@@
 \section*{Notes}
+
+\mk{Not exactly what we are talking about here, but there are a few good ideas/quotes in this blog post: https://rapidecology.com/2018/05/02/abandon-anova-type-experiments/}
+
+`` I’d like to propose that simple “comparison of means” experiments (those analyzed with a t-test or ANOVA) train our brains to think that this is the goal of science – to discover if an effect exists.
+--- But the goal of our science should be mechanistic and predictive models that make quantitative predictions that might be tested with experiments.''
+
+``The absurdity of the t-test or  ANOVA way of doing science is apparent if something like temperature and CO2 are the experimental factors – for example in the many global climate change studies.
+What in ecology or physiology or cell biology is not related to temperature and CO2?''
 

### 2018-09-25 doc.tex

@@
 whether we can clearly see that a correlation or between-group difference is positive or negative).
-We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
+We therefore suggest that results of null-hypothesis tests should be described using the language of ``statistical clarity'' rather than ``statistical significance''.
 We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.

### 2018-10-05 doc.tex
Update doc.tex

@@
 \textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
-We believe that a significant \mk{change word?}\jd{I did this on purpose (and also end with ``clarity'').
-Too cute?
-I kind of think it could help make the point.} part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
-
+We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
 Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
 whether we can clearly see that a correlation or between-group difference is positive or negative).
-We therefore suggest that results of null-hypothesis tests should be described using the language of ``statistical clarity'' rather than ``statistical significance''.
+We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
 We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.
@@
 
-\section*{Notes}
-
-\textbf{Structure:} I like the idea of two parallel boxes that have examples of language used in published papers on the
-left and corrected language on the right.
-Maybe three examples that correspond to four primary misinterpretations people
-make (zero effect, large p-values as ``more'' evidence for something, difference between clear and not clear is not clear,
-substantive significance)
-
-\textbf{Previous Work:} The bottom line is that \emph{\textbf{a lot}} has been said on the general topic of NHST and 
-p-values, though the idea of changing the language to clarity and retrieving the English definition of significant
-is novel.
-\citet{Bernardietal.2017} and \citet{McShaneetal.2017} have covered a lot of the history that is
-recounted below.
-It may be best to just cite these papers and state that concern about NHST and p-value abuse 
-remains high.
-\citep{Bernardietal.2017} present an analysis of the presence of errors in the interpretation of 
-results and ambiguity in language focused on NHST. Out of  They point out that these results are similar to the
-results from a similar review in the field of economics \citep{ZiliakandMcCloskey2008}.
-
-\textbf{Signs}.
-Who has said before that we test zero \emph{because} we want to know if we can see a sign clearly? If nobody, how much time do we want to spend on that point? 
-From \citet{robinson2001past}, which arose from \citet{jones2000sensible}: [instead of no difference, or no statistical difference] "authors should instead simply state that `the direction of the differences among the treatments was undetermined' or that `the sign of the correlation among the two variables was undetermined.'" --- That is, "If p is greater than 0.05, the conclusion is simply that the sign of the difference is not yet determined"
-
-\textbf{Notes:} A lot of this language assumes $H_{0} = 0$. Probably need to address clearly that many of these cited
-papers are based in psychology.
-I imagine we will want to anonymize quotes? (Though I kind of want to call out the null
-result short courses paper --- maybe as a point about non-significance and calling for reform)
-
-\textbf{Venue:} Forum in Trends in E and E: max 1200 words?
-Note in The American Naturalist: max 3000 words? Perspectives article in Nature?
-Rejected by Oikos forum!
-
 \clearpage
@@
 Books and articles proposing a deemphasis of the p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
-Yet, both reliance on NHST and the misinterpretation of results obtained from NHST remain high.
+This work includes pleas for an increased emphasis on effect sizes and confidence intervals, and points out that a zero, ``null effect'' does not exist in the vast majority of scientific fields \citep{Meehl1990, Tukey1991, Cohen1994}.
+Yet, p-values with out confidence intervals (or even effect sizes) and references to a ``null effect'' are still pervasive in high impact journals.
 
-In a 2017 meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 
-49\% interpreted non-significant effects as zero effects, and 44\% failed to report an effect size in a comprehensible 
-way.
-The misuse and misinterpretation of NHST is so pervasive that there has been a recent push for drastically reducing 
-\citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
-Others have called for a more
-strenuous significance threshold (e.g.
-$p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce
-the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold \citep{Ridleyetal.2007}.
+In a 2017 meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report an effect size in a comprehensible way.
+The misuse and misinterpretation of NHST is so frequent that there has been a recent push for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
+Others have called for a more strenuous significance threshold (e.g.
+$p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold \citep{Ridleyetal.2007}.
 
-Instead, we suggest that using the language of ``statistical clarity'' would help researchers escape the trap of accepting 
-the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for
-the continued use of NHST as a method of inference (e.g.
+\citet{Kramer2011} points out that \citep{ZiliakandMcCloskey2008} ask how could NHST possibly have survived "..if it is as idiotic as we and other critics have so long believed".
+We believe that NHST itself is not as idiotic as suggested; the idiocy associated with NHST is the language we use in describing it.
+A strong argument in favor of NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
+In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \cite{robinson2001past}.
+
+\section*{Statistical Clarity}
+
+We propose that using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for the continued use of NHST as a method of inference for for whether we can be confident of the \emph{sign} of a difference (e.g.
 see \citealt{Abelson1997} for arguments for NHST).
 The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the P value is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
-``Clarity,'' on the other hand, is an apt term for what hypothesis tests evaluate: a strong argument in favor of NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
-In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \cite{robinson2001past}.
+``Clarity,'' on the other hand, is an apt term for what hypothesis tests evaluate.
+\citet{Jones2000} and \citet{Robinson2001} suggest that researchers should report $p < 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''.
+While this is a step in the right direction, replacing ``significance'' with ``clarity'' is a more complete, direct, and universal change that will make sloppy thinking and misleading communication more difficult.
 
-Using the language of clarity makes sloppy thinking and misleading communication more difficult. 
-For example, we often see sentences like, ``X et al. showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
-In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about their study, not about the underlying processes \cite{CanWeCiteThis}.
-A better formulation would be ``X et al. did not find a significant effect of Y on Z.''
-This mistake seems harder to make using the language of clarity:  ``X et al. showed that the effect of Y on Z is unclear'' is awkward.
+We often see sentences like, ``X et al.
+showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
+In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about their study, not about the underlying processes \citep{HoenigandHeisey2001}.
+Indeed, because a p~value is a property of the data, and a true zero, $p < 0.05$ can be obtained for a very small effect with a large enough sample size.
+A better formulation would be ``X et al.
+did not find a significant effect of Y on Z.'' This mistake seems harder to make using the language of clarity:  ``X et al.
+showed that the effect of Y on Z is unclear'' is awkward.
 Similarly, ``We did not find a clear difference in response between the control and sham groups'' seems both more colloquially accurate and harder to transform into something misleading than ``We did not find a significant difference\ldots''.
@@
 
-\section*{Statistical Clarity}
-
-\mk{Language here needs a lot of work.
-Both in terms of clarity (haha) (use of ``confidence'' may be a bit confusing) and 
-because I am not sure that everything I am saying here is 100\% correct.
-Also not sure if this is how this section should
-start.
-Finally, portions of this have already been said in the paragraphs above.}
-
-A p~value is not a property of reality (e.g.  a biological phenomena), but is a property of a data set and the statistical test used.
-A p~value must therefore be interpreted and reported as a measure that quantifies our confidence about what we can see clearly about reality given our data.
-A $p < 0.05$ tells us that we are confident in in our ability to clearly see the sign
-of our effect (at an $\alpha = 0.05$ cutoff).
-While a direct illustration of this clarity is shown with the confidence 
-interval associated with $p < 0.05$, which will not overlap 0 (\mk{In nearly all cases?}), a p~value is a useful tool to 
-quantify this clarity.
-A p~value does not tell us about the substantive (e.g.
-biological) importance of our finding.
-Because
-the p~value is a property of the data, and a true zero,``null effect'' does not exist in the vast majority of scientific 
-fields \citep{Meehl1990, Tukey1991, Cohen1994}, $p < 0.05$ can be obtained for a very small effect with a large enough 
-sample size.
-Yet, references to a ``null effect'' can still be found in high impact journals \citep[e.g.][]{Feldonetal.2017}. 
-To emphasize that effects are not truly zero, descriptions of statistical results using the language of clarity should begin 
-with reference to the effect.
-For example, ``The difference between the control and treatment group was not statistically 
-clear.'' In Table~1 we provide examples from the literature of language that misinterprets p~values and a sensible way of
-rewriting these statements to reduce confusion.
-
-Another common mistake is using a larger p~value as stronger evidence for accepting the null hypothesis.
-A larger p value 
-actually corresponds to less clarity and thus the possibility of an undetected larger effect (see Table~1 for an example).
-In 
-2006 Gelman and Stern wrote that the difference between statistically significant and statistically non-significant is not 
-itself significant.
-Rewritten using ``clarity'' this statement indicates that if a single result is not statistically 
-clear, any comparison made between that unclear result and a clear result will not itself be a clear comparison.
-An example
-taken from the literature is in Table~1.
-
-\mk{My table formatting skills are pretty bad}
+Descriptions of statistical results using the language of clarity should begin with reference to the effect.
+For example, ``The difference between the control and treatment group was not statistically clear.'' In Table~1 we provide examples from the literature of language that misinterprets p~values in three different ways, and provide a sensible way of rewriting these statements to reduce confusion.
 
@@
 Following a shift in language, we suggest using a non-inferiority test to test for a small effect.
-Consider the following 
-example.
+Consider the following example.
 A hospital is considering switching from bulky, expensive surgical face masks to lighter weight, cheaper masks.
-A
-clinical trail that tests the effectiveness of both masks and finds $p > 0.05$ is not a success; this tells the hospital 
-that the difference between the masks is not statistically clear! What the hospital actually want to know is whether the 
-cheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}.
-This requires a $H_{0}$ that 
-defines the target difference in effectiveness of the two masks that the hospital is willing to accept to make the 
-transition.
-We note that this statistical test should be set up as a one-tailed test; the logical, \emph{a priori} 
-assumption is that the bulky, expensive masks are more effective.
-In this case, a $p < 0.05$ tells the hospital that the 
-difference between the new masks and old masks is small and that it they can proceed with the switch.
+A clinical trail that tests the effectiveness of both masks and finds $p > 0.05$ is not a success; this tells the hospital that the difference between the masks is not statistically clear!
+What the hospital actually want to know is whether thecheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}.
+This requires a $H_{0}$ that defines the target difference in effectiveness of the two masks that the hospital is willing to accept to make the transition.
+We note that this statistical test should be set up as a one-tailed test; the logical, \emph{a priori} assumption is that the bulky, expensive masks are more effective.
+In this case, a $p < 0.05$ tells the hospital that the difference between the new masks and old masks is small and that it they can proceed with the switch.
 
@@
 Accepting the null is especially common in diagnostic tests.
-For example, a Shapiro-Wilk test of normality that
-returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected
-from a complicated world and does depart from normality).
-Without the goal of picking on any paper in specific, 
-``...allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} 
-is common language that should be avoided.
+For example, a Shapiro-Wilk test of normality that returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected from a complicated world and does depart from normality).
+Without the goal of picking on any paper in specific, ``...allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} is common language that should be avoided.
 
-\subsection*{Previous suggestions}
+\subsection*{Previous suggestions are compatible with a change in language}
 
-Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016},
-we conclude with a plea for an increased emphasis on effect sizes and confidence intervals.
-However, we suggest that the
-use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing ambiguity
-from statements associated with $p < 0.05$. The statement ``The difference between our control and treatment groups was
-statistically clear ($p = 0.007$)'' is unambiguously incomplete; an effect size and confidence interval 
-is required to complete the story.
+Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}, we conclude with a plea for an increased emphasis on effect sizes and confidence intervals.
+However, we suggest that the use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing ambiguity from statements associated with $p < 0.05$.
+The statement ``The difference between our control and treatment groups was statistically clear ($p = 0.007$)'' is unambiguously incomplete; an effect size and confidence interval is required to complete the story.
 
-We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, 
-study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and 
-reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low 
-statistical power \citep[the "winners curse"][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}. 
-Additionally, we are in favor of writing a statistical journal that chronicles all steps in the analysis process 
-\citep{Kassetal.2016}, and clearly defining the boundary between results presented as inferences based on \emph{a priori}
-hypotheses and those from \emph{post hoc} data exploration.
-
-\section*{Lists}
-
-\begin{itemize}
-  \item Topics we may want to bring up
-	  \subitem Including a p~value helps to avoid type-S errors
-      \subitem usefulness of p --- use in splines: non-ridiculous standard to determine if we can see a pattern
-      \subitem difficulty in interpreting confidence intervals?
-\end{itemize}
-
-\begin{itemize}
-  \item Examples
-  \subitem Equating $p > 0.05$ with no difference: \citep{Ortegoetal.2007, Bukovinszkyetal.2017, Singhetal.2017, Sundinetal.2017}
-  \subitem Lack of clarity differentiating between biological and statistical significance: {Simonetal.2017}
-  \subitem Complete lack of effect sizes: \citep{Juriadoetal.2017}
-  \subitem Setting out to accept the null: \citep{Karulinetal.2015}
-  \subitem ``...establish the \emph{a priori} selection of an effect level that is considered unacceptably toxic:'' \citep{Dentonetal.2011}
-  \subitem With the \emph{correlation coefficient} for males and females (but significance for only one sex---``substrate 
-  choice correlated significantly with food choice in males'') the authors go on to describe biologically why the 
-  correlation would be significant for males but not females.
-\citep{MerilaitaandJormalainen1997}
-\end{itemize}
-
-\begin{itemize}
-  \item To do
-  	\subitem unsort bib for convenient lookup of types of cites
-    \subitem links in bib to pdfs
-\end{itemize}
+We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the "winners curse"][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
+Additionally, we are in favor of writing a statistical journal that chronicles all steps in the analysis process \citep{Kassetal.2016}, and clearly defining the boundary between results presented as inferences based on \emph{a priori} hypotheses and those from \emph{post hoc} data exploration.
 

### 2018-10-08 doc.tex
various tweaks to ms

@@
 We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
-Although null-hypothesis tests have limitations, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
+Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
 whether we can clearly see that a correlation or between-group difference is positive or negative).
-We therefore suggest that p-values resulting from null-hypothesis tests be described using the language of ``statistical clarity'' rather than ``statistical significance''.
-We believe that this simple linguistic change has the potential to substantially enhance clarity in statistical communication.
+We therefore suggest that \pvals resulting from null-hypothesis tests be described using the language of statistical \emph{clarity} rather than statistical \emph{significance}.
+This simple semantic change could substantially enhance clarity in statistical communication.
 
@@
 
-For nearly a century statisticians and scientists have described the shortcomings of Null Hypothesis Significance Testing (NHST) \citep[see][]{Cohen1994}.
-Books and articles proposing a deemphasis of the p~value in favor of effect sizes and confidence intervals have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
-This work includes pleas for an increased emphasis on effect sizes and confidence intervals, and points out that a zero, ``null effect'' does not exist in the vast majority of scientific fields \citep{Meehl1990, Tukey1991, Cohen1994}.
-Yet, p-values with out confidence intervals (or even effect sizes) and references to a ``null effect'' are still pervasive in high impact journals.
+Statisticians and scientists have bemoaned the shortcomings of null hypothesis significance testing (NHST) for nearly a century \citep{Cohen1994}.
+Books and articles proposing the de-emphasis or abandonment of the \pval have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
+These works plead for a focus on effect sizes and confidence intervals, and point out that a zero, ``null effect'' is unrealistic or impossible in most fields outside of the hard physical sciences \citep{Meehl1990, Tukey1991, Cohen1994}.
+Yet, \pvals without confidence intervals (or even effect sizes) and references to null effects still pervade the scientific literature at all levels up to and including high-impact journals.
 
-In a 2017 meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report an effect size in a comprehensible way.
+In a meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report a comprehensible effect size.
 The misuse and misinterpretation of NHST is so frequent that there has been a recent push for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
-Others have called for a more strenuous significance threshold (e.g.
-$p < 0.005$: \citealt{Benjaminetal.2018}); however, this change is unlikely to reduce the misuse and misinterpretation of p~values, or the publication bias imposed by any p~value threshold \citep{Ridleyetal.2007}.
+Other prescriptions have included calls for the complete abandonment of frequentist statistics \bmb{CITE: is it OK to include this here, or it too distracting?}, or for the use of a more strenuous significance threshold (e.g.
+$p < 0.005$: \citealt{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.
 
-\citet{Kramer2011} points out that \citep{ZiliakandMcCloskey2008} ask how could NHST possibly have survived "..if it is as idiotic as we and other critics have so long believed".
+\citet{Kramer2011} points out that \citep{ZiliakandMcCloskey2008} ask how could NHST possibly have survived ``\ldots if it is as idiotic as we and other critics have so long believed''.
 We believe that NHST itself is not as idiotic as suggested; the idiocy associated with NHST is the language we use in describing it.
@@
 
-We propose that using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for the continued use of NHST as a method of inference for for whether we can be confident of the \emph{sign} of a difference (e.g.
+Using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for the continued use of NHST as a method of inference for for whether we can be confident of the sign of a difference (e.g.
 see \citealt{Abelson1997} for arguments for NHST).
-The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the P value is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
-``Clarity,'' on the other hand, is an apt term for what hypothesis tests evaluate.
-\citet{Jones2000} and \citet{Robinson2001} suggest that researchers should report $p < 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''.
-While this is a step in the right direction, replacing ``significance'' with ``clarity'' is a more complete, direct, and universal change that will make sloppy thinking and misleading communication more difficult.
+The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
+``Clarity,'' on the other hand, is an apt term for what NHST actually evaluates.
+\citet{jones2000sensible} and \citet{robinson2001past} suggest that researchers should report $p < 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''.
+While this is a step in the right direction, replacing ``significance'' with ``clarity'' is a more complete, direct, and universal change that will improve communication and reduce sloppy thinking.
 
@@
 showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
-In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about their study, not about the underlying processes \citep{HoenigandHeisey2001}.
-Indeed, because a p~value is a property of the data, and a true zero, $p < 0.05$ can be obtained for a very small effect with a large enough sample size.
+In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about \emph{their study}, not about the underlying processes \citep{HoenigandHeisey2001}.
+Indeed, because a \pval is a property of the data, $p < 0.05$ can be obtained for a very small effect with a large enough sample size.
 A better formulation would be ``X et al.
-did not find a significant effect of Y on Z.'' This mistake seems harder to make using the language of clarity:  ``X et al.
+did not find a significant effect of Y on Z.'' This mistake is harder to make using the language of clarity:  ``X et al.
 showed that the effect of Y on Z is unclear'' is awkward.
-Similarly, ``We did not find a clear difference in response between the control and sham groups'' seems both more colloquially accurate and harder to transform into something misleading than ``We did not find a significant difference\ldots''.
-\citet{Bernardietal.2017} argued that ``...sociological and social significance are sacrificed on the altar of statistical significance''.
-Describing statistical tests in terms of clarity could allow ``significant'' to reclaim its common English definition, and reduce conflation between statistical results and substantive significance.
+Similarly, ``We did not find a clear difference in response between the control and sham groups'' is both more colloquial and harder to transform into a misleading statement than ``We did not find a significant difference \ldots''.
+\citet{Bernardietal.2017} complained that ``\ldots sociological and social significance are sacrificed on the altar of statistical significance''.
+Describing statistical tests in terms of clarity would allow ``significant'' to reclaim its common English definition and reduce conflation between statistical results and substantive significance.
 
 Descriptions of statistical results using the language of clarity should begin with reference to the effect.
-For example, ``The difference between the control and treatment group was not statistically clear.'' In Table~1 we provide examples from the literature of language that misinterprets p~values in three different ways, and provide a sensible way of rewriting these statements to reduce confusion.
+For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows examples from the literature of language that misinterpret \pvals in three different ways, and demonstrates how to rewrite these statements in the language of clarity.
 
+\newcommand{\ourcomment}[1]{[\emph{#1}]}
+\begin{table}
 \setlength\tabcolsep{1cm}.
 \begin{tabular}{p{7.0cm}p{7.0cm}}
-Language from published articles & Rewritten using ``clarity'' \\
+\textbf{Language from published articles} & \textbf{Rewritten using ``clarity''} \\
 \hline\\
 
-\multicolumn{2}{c}{$\mathbf{p > 0.05 \neq}$ \textbf{zero effect}} \\
+\multicolumn{2}{c}{\emph{\textbf{Accepting the null hypothesis ($\boldsymbol{p > 0.05 \nRightarrow}$ no effect)}}} \\
+\hline
 
@@
 
+\rowcolor{lightgray}
 There was no effect of elevated carbon dioxide on reproductive behaviors 
@@
 The finding that species richness showed no significant relationship with the area of available habitat is surprising because richness is usually strongly influenced by landscape context 
-& Although species richness is usually strongly influenced by landscape context, in the present study this relationship was not statistically clear 
+& Although species richness is usually strongly influenced by landscape context, we were unable to find a statistically clear relationship in this study
 \\ \\
 
-\multicolumn{2}{c}{\textbf{Comparing P~values}}
+\multicolumn{2}{c}{\emph{\textbf{Inferring weak effects from large \pvals}}}
 \\
-
+\hline
+%% left ``P values'' unchanged here (not \pvals) since it's a quotation
 \ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
-& \ldots\ differences between treatment and control groups were not statistically clear ($P > 0.05$)
+& \ldots\ differences between treatment and control groups were not statistically clear ($P > 0.05$) \ourcomment{confidence intervals would also be valuable here!}
 \\ \\
 
-\multicolumn{2}{c}{\textbf{The difference between ``clear'' and ``not clear'' is ``not clear''}}
+\multicolumn{2}{c}{\emph{\textbf{The difference between ``clear'' and ``not clear'' is not clear}} \citep{GelmanandStern2006}}
 \\
+\hline
 
 This correlation was significant in males ($\rho=0.35$, P \textless 0.05) but not females ($\rho=0.35$, NS).
-\ldots [Afterwards the assumption is that a difference between males and females has been demonstrated]
-& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots [This phrasing may suggest to the authors that confidence intervals are called for.]
+\ldots \ourcomment{The authors later assume that they have demonstrated a difference between males and females}
+& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{This phrasing may suggest to the authors that confidence intervals are called for.}
 \\
-
-...risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
+\rowcolor{lightgray}
+\ldots risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
 (adjusted OR 2.99, 95\% CI 1.33–6.74), but no association was found between HCV coinfection and low BMD in men 
-(adjusted OR 1.26, 95\% CI 0.75–2.10). ... While the authors do not directly compare men and women they do state: 
+(adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots  \ourcomment{The authors do not directly compare men and women, but they state:}
 The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men 
@@
 & 
-..risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
+\ldots  risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
 (adjusted OR 2.99, 95\% CI 1.33–6.74), but the association between HCV coinfection and low BMD in men was not
-statistically clear (adjusted OR 1.26, 95\% CI 0.75–2.10). ... Pursuing the biological importance of HIV on BMD in 
-women and not men is premature given these statistics and requires further study.
+statistically clear (adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots  Pursuing biological differences between women and men in the effect of HIV on BMD would be premature given these results.
 \\
 \end{tabular}
-   \captionof{table}{Rewriting misinformed language in the published literature using our proposed updated language.}
+\captionof{table}{Examples of misinformed language in peer-reviewed papers (citations withheld out of courtesy, available by request) using our proposed  language of clarity.}
+\label{quotetab}
+\end{table}
 
@@
 
+\bmb{would be good to have a citation here; do any of the ``best practices''/NHST criticisms bring up N-I tests? If not, is there a good intro reference?}
 Following a shift in language, we suggest using a non-inferiority test to test for a small effect.
@@
 A clinical trail that tests the effectiveness of both masks and finds $p > 0.05$ is not a success; this tells the hospital that the difference between the masks is not statistically clear!
-What the hospital actually want to know is whether thecheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}.
+What the hospital actually want to know is whether the cheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}.
 This requires a $H_{0}$ that defines the target difference in effectiveness of the two masks that the hospital is willing to accept to make the transition.
@@
 For example, a Shapiro-Wilk test of normality that returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected from a complicated world and does depart from normality).
-Without the goal of picking on any paper in specific, ``...allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} is common language that should be avoided.
+Without the goal of picking on any paper in specific, ``\ldots allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} is common language that should be avoided.
 
@@
 
-We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the "winners curse"][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
-Additionally, we are in favor of writing a statistical journal that chronicles all steps in the analysis process \citep{Kassetal.2016}, and clearly defining the boundary between results presented as inferences based on \emph{a priori} hypotheses and those from \emph{post hoc} data exploration.
+We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
+Additionally, we support the idea of writing a statistical journal that chronicles all steps in the analysis process \citep{Kassetal.2016}, and clearly defining the boundary between results presented as inferences based on \emph{a priori} hypotheses and those from \emph{post hoc} data exploration.
 

### 2018-10-08 doc.tex
a few more quick comments

@@
 whether we can clearly see that a correlation or between-group difference is positive or negative).
-We therefore suggest that \pvals resulting from null-hypothesis tests be described using the language of statistical \emph{clarity} rather than statistical \emph{significance}.
+We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than statistical ``significance''.
 This simple semantic change could substantially enhance clarity in statistical communication.
@@
 Books and articles proposing the de-emphasis or abandonment of the \pval have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
-These works plead for a focus on effect sizes and confidence intervals, and point out that a zero, ``null effect'' is unrealistic or impossible in most fields outside of the hard physical sciences \citep{Meehl1990, Tukey1991, Cohen1994}.
-Yet, \pvals without confidence intervals (or even effect sizes) and references to null effects still pervade the scientific literature at all levels up to and including high-impact journals.
+These works plead for a focus on effect sizes and confidence intervals, and point out that null effects that truly have zero magnitude are unrealistic or impossible in most fields outside of the hard physical sciences \citep{Meehl1990, Tukey1991, Cohen1994}.
+Yet, \pvals without confidence intervals (or even effect sizes) and references to null effects still pervade the scientific literature at all levels up to and including articles in high-impact journals.
 
 In a meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report a comprehensible effect size.
-The misuse and misinterpretation of NHST is so frequent that there has been a recent push for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
-Other prescriptions have included calls for the complete abandonment of frequentist statistics \bmb{CITE: is it OK to include this here, or it too distracting?}, or for the use of a more strenuous significance threshold (e.g.
+The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
+Other prescriptions have included the complete abandonment of frequentist statistics \bmb{CITE: is it OK to include this here, or it too distracting?}, or the use of a stricter significance threshold (e.g.
 $p < 0.005$: \citealt{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.
 
-\citet{Kramer2011} points out that \citep{ZiliakandMcCloskey2008} ask how could NHST possibly have survived ``\ldots if it is as idiotic as we and other critics have so long believed''.
-We believe that NHST itself is not as idiotic as suggested; the idiocy associated with NHST is the language we use in describing it.
-A strong argument in favor of NHST is that testing the null hypothesis (even though we often know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
-In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \cite{robinson2001past}.
+\citet{Kramer2011} points out Ziliak and McCloskey's (\citeyear{ZiliakandMcCloskey2008}) query how could NHST possibly have survived ``\ldots if it is as idiotic as we and other critics have so long believed''.
+We believe that NHST itself \bmb{[although dangerously prone to misuse?]} is not as idiotic as suggested; the idiocy associated with NHST is the language we use in describing it.
+A strong argument in favor of NHST is that testing the null hypothesis (even though we usually know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
+In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}.
 
@@
 
-Using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for the continued use of NHST as a method of inference for for whether we can be confident of the sign of a difference (e.g.
-see \citealt{Abelson1997} for arguments for NHST).
+Using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with NHST, and allow for the continued use of NHST to determine whether we can be confident about the sign of a difference (e.g.
+see \citealt{Abelson1997} for arguments for NHST \bmb{what's in Abelson?
+How much of our argument do they anticipate?}).
 The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
@@
 showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
-In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about \emph{their study}, not about the underlying processes \citep{HoenigandHeisey2001}.
-Indeed, because a \pval is a property of the data, $p < 0.05$ can be obtained for a very small effect with a large enough sample size.
+In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about \emph{their particular study}, not about the underlying processes \citep{HoenigandHeisey2001}.
+Indeed, because a \pval is a property of the data, $p < 0.05$ can be obtained for a very small effect with a sufficently large  sample, or for a very large effect with a sufficiently small or noisy sample.
 A better formulation would be ``X et al.
@@
 Descriptions of statistical results using the language of clarity should begin with reference to the effect.
-For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows examples from the literature of language that misinterpret \pvals in three different ways, and demonstrates how to rewrite these statements in the language of clarity.
+For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows published examples of statements that misinterpret \pvals in three different ways and demonstrates how to rephrase them in the language of clarity.
 
@@
 Toxins accumulate after acute exposure but have no effect on behaviour
-& Toxins accumulate after acute exposure but effects on behaviour are statistically unclear
+& Toxins accumulate after acute exposure but their effects on behaviour are statistically unclear
 \\
@@
 
-\multicolumn{2}{c}{\emph{\textbf{Inferring weak effects from large \pvals}}}
+\multicolumn{2}{c}{\emph{\textbf{Inferring weak effects from large \pvals}} \citep{WassersteinandLazar2016}}
 \\
@@
 \ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
-& \ldots\ differences between treatment and control groups were not statistically clear ($P > 0.05$) \ourcomment{confidence intervals would also be valuable here!}
+& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{confidence intervals would also be valuable here!}
 \\ \\
@@
 This correlation was significant in males ($\rho=0.35$, P \textless 0.05) but not females ($\rho=0.35$, NS).
-\ldots \ourcomment{The authors later assume that they have demonstrated a difference between males and females}
+\ldots \ourcomment{The authors later write as though they have demonstrated a difference between males and females}
 & Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{This phrasing may suggest to the authors that confidence intervals are called for.}
@@
 \end{tabular}
-\captionof{table}{Examples of misinformed language in peer-reviewed papers (citations withheld out of courtesy, available by request) using our proposed  language of clarity.}
+\captionof{table}{Examples of misinformed language in peer-reviewed papers (citations withheld out of courtesy, available by request) using our proposed  language of clarity.
+\bmb{do we want to comment on our search strategy?
+Doesn't need to be formal [this isn't a meta-analysis], but might be of interest to readers}}
 \label{quotetab}
@@
 
-\section*{Closing Comments}
+\section*{Further recommendations}
+
+\bmb{this section seems a bit ``grab-baggy''.
+Can we restructure it so it feels more coherent?
+I don't mind including these points, but I would rather leave them out than dilute the message/bog the reader down.
+Do we want to mention the more difficult case of NHST on non-negative domains (i.e.
+joint tests of multiple parameters, tests of variances, etc., where we can't interpret \pval as clarity about signs?)}
+
+\subsection*{Focal vs non-focal hypotheses}
+
+\bmb{I'd like to consider omitting the next (sub)section.
+The connection between the title and the text is not very clear, and I don't think it's the most important point.
+(If it can be made clear and punchy I don't mind including it.) Interesting discussion of using Shapiro-Wilk $W$ as an effect size (spoiler: it might be a bad idea)  \underline{\href{https://stats.stackexchange.com/questions/2492/is-normality-testing-essentially-useless}{here}}, and general discussion of uselessness of Normality testing \underline{\href{https://stats.stackexchange.com/questions/289136/is-the-shapiro-wilk-test-w-an-effect-size}{here}}.
+Also, we should be able to invent some  typically bad wording without breaking our protocol and mentioning a particular article here: ``Wording such as `The Shapiro-Wilk test gave $p>0.05$, allowing us to conclude that the data are normally distributed' \ldots''}
+
+Accepting the null is especially common when researchers perform diagnostic tests of the assumptions of statistical tests.
+For example, a Shapiro-Wilk test of normality that returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected from a complicated world and does depart from normality).
+Without the goal of picking on any paper in specific, ``\ldots allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} is common language that should be avoided.
 
@@
 
-\bmb{would be good to have a citation here; do any of the ``best practices''/NHST criticisms bring up N-I tests? If not, is there a good intro reference?}
-Following a shift in language, we suggest using a non-inferiority test to test for a small effect.
+\bmb{(1) would be good to have a citation here; do any of the ``best practices''/NHST criticisms bring up N-I tests?
+If not, is there a good intro reference?
+If it's \emph{not} widely stated in the NHST-criticism literature, that strengthens the case for including it here.
+(2) This needs more context, if we include it; if as suggested it's not widely pointed out in the NHST-crit lit, ``One tool that is well known in the biostatistical world but underappreciated in more applied areas \ldots''.
+Or, ``Reporting CIs provides meaningful information about how small a measured effect might be \ldots if researchers want to be perform a formal test that biological effects are small \ldots'' As I understand it non-inferiority tests are directed; could one construct a p-value for an \emph{unsigned} test, i.e.
+trying to show that $|\beta|<T$ for some pre-specified $T$?
+Or am I sneaking up on an \emph{a priori} power analysis?}
+
+Following a shift in language, we suggest using a non-inferiority test to test for the hypothesis that biological effects are small.
 Consider the following example.
@@
 
-\subsection*{Focal vs non-focal hypotheses}
-
-Accepting the null is especially common in diagnostic tests.
-For example, a Shapiro-Wilk test of normality that returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected from a complicated world and does depart from normality).
-Without the goal of picking on any paper in specific, ``\ldots allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} is common language that should be avoided.
-
 \subsection*{Previous suggestions are compatible with a change in language}
 
+\bmb{I'd be OK with making this section alone be our Conclusions (if we don't want to clean up/improve the previous sections)}
 Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}, we conclude with a plea for an increased emphasis on effect sizes and confidence intervals.
-However, we suggest that the use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing ambiguity from statements associated with $p < 0.05$.
-The statement ``The difference between our control and treatment groups was statistically clear ($p = 0.007$)'' is unambiguously incomplete; an effect size and confidence interval is required to complete the story.
+However, we suggest that the use of ``statistical clarity'' reinforces the need for confidence intervals and effect sizes by making it clearer that bald statements about \pvals are insufficient.
+The statement ``The difference between our control and treatment groups was statistically clear ($p = 0.007$)'' is unambiguously incomplete; an effect size and confidence interval are required to complete the story.
 
 We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
-Additionally, we support the idea of writing a statistical journal that chronicles all steps in the analysis process \citep{Kassetal.2016}, and clearly defining the boundary between results presented as inferences based on \emph{a priori} hypotheses and those from \emph{post hoc} data exploration.
+Additionally, we support the idea of writing a statistical journal that chronicles all steps in the analytical process \citep{Kassetal.2016}, and clearly delineating the boundary between inferences based on \emph{a priori} hypotheses and discoveries from \emph{post hoc} data exploration.
+
+Whether or not our recommendations are broadly adopted by authors, reviewers, and editors, they can be useful for individual researchers who want to help themselves think clearly about NHST results.
+We have found that rephrasing NHST statements that we encounter (in the literature, or in seminar presentations) in terms of clarity has helped us to correctly interpret their meanings.
 

### 2018-10-09 doc.tex

@@
 
-Using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with NHST, and allow for the continued use of NHST to determine whether we can be confident about the sign of a difference (e.g.
+Using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for the continued use of NHST as a method of inference for for whether we can be confident of the sign of a difference (e.g.
 see \citealt{Abelson1997} for arguments for NHST \bmb{what's in Abelson?
@@
 \end{tabular}
-\captionof{table}{Examples of misinformed language in peer-reviewed papers (citations withheld out of courtesy, available by request) using our proposed  language of clarity.
-\bmb{do we want to comment on our search strategy?
-Doesn't need to be formal [this isn't a meta-analysis], but might be of interest to readers}}
+\captionof{table}{Examples of misinformed language in peer-reviewed papers (citations withheld out of courtesy, available by request) using our proposed  language of clarity.}
 \label{quotetab}
@@
 Can we restructure it so it feels more coherent?
-I don't mind including these points, but I would rather leave them out than dilute the message/bog the reader down.
-Do we want to mention the more difficult case of NHST on non-negative domains (i.e.
-joint tests of multiple parameters, tests of variances, etc., where we can't interpret \pval as clarity about signs?)}
+I don't mind including these points, but I would rather leave them out than dilute the message/bog the reader down.}
 

### 2018-10-09 doc.tex
Many suggestions

@@
 The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
-Other prescriptions have included the complete abandonment of frequentist statistics \bmb{CITE: is it OK to include this here, or it too distracting?}, or the use of a stricter significance threshold (e.g.
+Other prescriptions have included the complete abandonment of frequentist statistics \citeneeded, or the use of a stricter significance threshold (e.g.
 $p < 0.005$: \citealt{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.
 
-\citet{Kramer2011} points out Ziliak and McCloskey's (\citeyear{ZiliakandMcCloskey2008}) query how could NHST possibly have survived ``\ldots if it is as idiotic as we and other critics have so long believed''.
-We believe that NHST itself \bmb{[although dangerously prone to misuse?]} is not as idiotic as suggested; the idiocy associated with NHST is the language we use in describing it.
-A strong argument in favor of NHST is that testing the null hypothesis (even though we usually know that it's false, and can never prove that it's true) is a proxy for asking whether we can see a difference clearly.
+Here, we argue that NHST remains useful, and that pervasive misuse can be reduced through a linguistic change: using the language of statistical ``clarity'' instead of statistical ``significance''.
+
+\section*{The null hypothesis is false}
+
+In most biological studies, the null hypothesis is known or believed to not be strictly true.
+Even in cases where the null hypothesis is sensible (e.g., particle physics) \pval testing does not provide a route to confirmation.
+This being the case, it is worth asking how NHST has survived `` if it is as idiotic as \ldots long believed''. 
+\jd{Why does Morgan cite Kramer?} \citet{Kramer2011}.
+
+The value of NHST can be seen in something like a permutation-based t-test \cite{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. 
+More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it.
 In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
+In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether something has been seen clearly.
+
+The ``idiocy'', if any, comes in the interpretive step.
+A statistical fact (``we have \emph{seen} a difference between the groups'', which should immediately prompt the question ``what have you learned \emph{about} that difference?'') is interpreted as a scientific fact (``there \emph{is} a `significant' difference between the groups), which is often seen as an end in itself: ``we showed that the groups differ''.
+
+\section*{The \pval is a property of the study}
+
+We often see sentences like, ``X et al.
+showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
+In fact, the sentence is erroneous even before we get to the implication: significance tests provide information about \emph{a data set} -- that is, about a study, not about the study system \citep{HoenigandHeisey2001}.
+Indeed, a very small effect can lead to $p < 0.05$, when data is abundant (or noise is small); or a very large one can lead to $p > 0.05$ when the sample is small or noisy.
+
+The statement ``X et al. showed that Y has a statistically significant effect on Z'' is similarly misleading.
+Frequentist statistics effectively assume that the effect is present (or at least, admit that it can't be disproven).
+The question is whether it is seen in a particular data set.
+The statement ``X et al. were able to see the effect of Y on Z'' is not only more accurate, but it appropriately implies that something is missing: \emph{What} effect did they see?
 
@@
 
-Using the language of ``statistical clarity'' would help researchers escape the trap of accepting the null hypothesis, reduce multiple types of misinterpretation associated with accepting the null hypothesis, and allow for the continued use of NHST as a method of inference for for whether we can be confident of the sign of a difference (e.g.
-see \citealt{Abelson1997} for arguments for NHST \bmb{what's in Abelson?
+The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \citealt{Abelson1997} for arguments for NHST \bmb{what's in Abelson?
 How much of our argument do they anticipate?}).
@@
 ``Clarity,'' on the other hand, is an apt term for what NHST actually evaluates.
-\citet{jones2000sensible} and \citet{robinson2001past} suggest that researchers should report $p < 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''.
-While this is a step in the right direction, replacing ``significance'' with ``clarity'' is a more complete, direct, and universal change that will improve communication and reduce sloppy thinking.
+\citet{jones2000sensible} and \citet{robinson2001past} suggest that researchers should report $p > 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''.
+This is a step in the right direction.
+Replacing ``significance'' with ``clarity'' takes this further, and has the promise to substantially improve statistical communication.
 
-We often see sentences like, ``X et al.
-showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
-In fact, the sentence is erroneous even before we get to the implication: X et al.'s significance test provides information about \emph{their particular study}, not about the underlying processes \citep{HoenigandHeisey2001}.
-Indeed, because a \pval is a property of the data, $p < 0.05$ can be obtained for a very small effect with a sufficently large  sample, or for a very large effect with a sufficiently small or noisy sample.
-A better formulation would be ``X et al.
-did not find a significant effect of Y on Z.'' This mistake is harder to make using the language of clarity:  ``X et al.
-showed that the effect of Y on Z is unclear'' is awkward.
+For example, the sentence ``X et al.
+showed that the effect of Y on Z is statistically unclear'', is noticeably awkward.
+It seems less like a statement about the study system, and suggests the more straightforward ``did not find a statistically clear effect.''
 Similarly, ``We did not find a clear difference in response between the control and sham groups'' is both more colloquial and harder to transform into a misleading statement than ``We did not find a significant difference \ldots''.
@@
 
-\rowcolor{lightgray}
+\rowcolor{vlg}
 There was no effect of elevated carbon dioxide on reproductive behaviors 
@@
 \\
-\rowcolor{lightgray}
+\rowcolor{vlg}
 \ldots risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
 (adjusted OR 2.99, 95\% CI 1.33–6.74), but no association was found between HCV coinfection and low BMD in men 
-(adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots  \ourcomment{The authors do not directly compare men and women, but they state:}
-The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men 
-remain unclear.
+(adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots 
+The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men remain unclear.
 & 
@@
 \end{tabular}
-\captionof{table}{Examples of misinformed language in peer-reviewed papers (citations withheld out of courtesy, available by request) using our proposed  language of clarity.}
+\captionof{table}{Examples of misleading language in peer-reviewed papers (citations available by request), and revisions using our proposed  language of clarity.}
 \label{quotetab}
@@
 
-\section*{Further recommendations}
+\subsection*{Conclusions}
 
-\bmb{this section seems a bit ``grab-baggy''.
-Can we restructure it so it feels more coherent?
-I don't mind including these points, but I would rather leave them out than dilute the message/bog the reader down.}
+We believe that NHST is useful as a simple, robust way to ask whether an effect can be seen clearly in a particular data set \citep{robinson2001past}, and that careful, clarity-based language can reduce misinterpretation and miscommunication.
 
-\subsection*{Focal vs non-focal hypotheses}
+We agree with \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}, that scientific communication and understanding will be improved by a shift away from \pvals to effect sizes and confidence intervals.
+We argue that the use of ``statistical clarity'' reinforces the need for confidence intervals and effect sizes by making it clearer that bald statements about \pvals are insufficient. 
+The statement ``The difference between our control and treatment groups was not statistically clear ($p = 0.30$)'' is noticeably incomplete; an effect size and confidence interval are required to complete the story.
 
-\bmb{I'd like to consider omitting the next (sub)section.
-The connection between the title and the text is not very clear, and I don't think it's the most important point.
-(If it can be made clear and punchy I don't mind including it.) Interesting discussion of using Shapiro-Wilk $W$ as an effect size (spoiler: it might be a bad idea)  \underline{\href{https://stats.stackexchange.com/questions/2492/is-normality-testing-essentially-useless}{here}}, and general discussion of uselessness of Normality testing \underline{\href{https://stats.stackexchange.com/questions/289136/is-the-shapiro-wilk-test-w-an-effect-size}{here}}.
-Also, we should be able to invent some  typically bad wording without breaking our protocol and mentioning a particular article here: ``Wording such as `The Shapiro-Wilk test gave $p>0.05$, allowing us to conclude that the data are normally distributed' \ldots''}
-
-Accepting the null is especially common when researchers perform diagnostic tests of the assumptions of statistical tests.
-For example, a Shapiro-Wilk test of normality that returns $p > 0.05$ means that it is statistically unclear how the data departs from normality (the data is collected from a complicated world and does depart from normality).
-Without the goal of picking on any paper in specific, ``\ldots allowing us to accept the null hypothesis about the normal spot count distribution.'' \citep{Karulinetal.2015} is common language that should be avoided.
-
-\subsection*{Non-inferiority tests}
-
-\bmb{(1) would be good to have a citation here; do any of the ``best practices''/NHST criticisms bring up N-I tests?
-If not, is there a good intro reference?
-If it's \emph{not} widely stated in the NHST-criticism literature, that strengthens the case for including it here.
-(2) This needs more context, if we include it; if as suggested it's not widely pointed out in the NHST-crit lit, ``One tool that is well known in the biostatistical world but underappreciated in more applied areas \ldots''.
-Or, ``Reporting CIs provides meaningful information about how small a measured effect might be \ldots if researchers want to be perform a formal test that biological effects are small \ldots'' As I understand it non-inferiority tests are directed; could one construct a p-value for an \emph{unsigned} test, i.e.
-trying to show that $|\beta|<T$ for some pre-specified $T$?
-Or am I sneaking up on an \emph{a priori} power analysis?}
-
-Following a shift in language, we suggest using a non-inferiority test to test for the hypothesis that biological effects are small.
-Consider the following example.
-A hospital is considering switching from bulky, expensive surgical face masks to lighter weight, cheaper masks.
-A clinical trail that tests the effectiveness of both masks and finds $p > 0.05$ is not a success; this tells the hospital that the difference between the masks is not statistically clear!
-What the hospital actually want to know is whether the cheaper, lighter masks are \emph{only a little bit worse than the bulky, expensive masks}.
-This requires a $H_{0}$ that defines the target difference in effectiveness of the two masks that the hospital is willing to accept to make the transition.
-We note that this statistical test should be set up as a one-tailed test; the logical, \emph{a priori} assumption is that the bulky, expensive masks are more effective.
-In this case, a $p < 0.05$ tells the hospital that the difference between the new masks and old masks is small and that it they can proceed with the switch.
-
-\subsection*{Previous suggestions are compatible with a change in language}
-
-\bmb{I'd be OK with making this section alone be our Conclusions (if we don't want to clean up/improve the previous sections)}
-Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}, we conclude with a plea for an increased emphasis on effect sizes and confidence intervals.
-However, we suggest that the use of ``statistical clarity'' reinforces the need for confidence intervals and effect sizes by making it clearer that bald statements about \pvals are insufficient.
-The statement ``The difference between our control and treatment groups was statistically clear ($p = 0.007$)'' is unambiguously incomplete; an effect size and confidence interval are required to complete the story.
-
+\jd{Not sure how this P. fits in, either. I guess I'd like to keep it, though.}
 We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
@@
 Whether or not our recommendations are broadly adopted by authors, reviewers, and editors, they can be useful for individual researchers who want to help themselves think clearly about NHST results.
-We have found that rephrasing NHST statements that we encounter (in the literature, or in seminar presentations) in terms of clarity has helped us to correctly interpret their meanings.
+We have found that rephrasing NHST statements that we encounter (in the literature, or in seminar presentations) in terms of clarity has already helped us with both interpretation and communication.
 
-\subsection*{Acknowledgements}
+\subsection*{Acknowledgments}
 

### 2018-10-09 doc.tex
GoodBook chapter ref

@@
 
-The value of NHST can be seen in something like a permutation-based t-test \cite{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. 
+The value of NHST can be seen in something like a permutation-based t-test \cite[Chapter 1]{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger. 
 More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it.

### 2018-10-09 doc.tex

@@
 The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
-Other prescriptions have included the complete abandonment of frequentist statistics \citeneeded, or the use of a stricter significance threshold (e.g.
+Other prescriptions have included the complete abandonment of frequentist statistics \citep{The2011}, or the use of a stricter significance threshold (e.g.
 $p < 0.005$: \citealt{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.
@@
 In most biological studies, the null hypothesis is known or believed to not be strictly true.
-Even in cases where the null hypothesis is sensible (e.g., particle physics) \pval testing does not provide a route to confirmation.
-This being the case, it is worth asking how NHST has survived `` if it is as idiotic as \ldots long believed''. 
+Even in cases where the null hypothesis is sensible \citep[e.g., particle physics][]{Staley2017} \pval testing does not provide a route to confirmation.
+This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed''. 
 \jd{Why does Morgan cite Kramer?} \citet{Kramer2011}.
@@
 This is a step in the right direction.
-Replacing ``significance'' with ``clarity'' takes this further, and has the promise to substantially improve statistical communication.
+Replacing ``significance'' with ``clarity'' takes this idea further, and has the promise to substantially improve statistical communication.
 

### 2018-10-09 doc.tex
BMB comments/tweaks

@@
 Even in cases where the null hypothesis is sensible \citep[e.g., particle physics][]{Staley2017} \pval testing does not provide a route to confirmation.
+\bmb{¿ clarify ?}
 This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed''. 
-\jd{Why does Morgan cite Kramer?} \citet{Kramer2011}.
+\jd{Why does Morgan cite Kramer?}
+\bmb{perhaps [IIRC] because it was an indirect ref?}
+\citet{Kramer2011}.
 
@@
 In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
-In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether something has been seen clearly.
+In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
 

### 2018-10-09 doc.tex
Update doc.tex
correct statement about 'multi-way ANOVA'

@@
 In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
-In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
+In other cases (e.g., testing the overall effect of a categorical predictor with more than two levels), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
 

### 2018-10-09 doc.tex
Meeting with Morgan and Ben

--- 2018-10-09 doc.tex
@@
 In most biological studies, the null hypothesis is known or believed to not be strictly true.
-Even in cases where the null hypothesis is sensible \citep[e.g., particle physics][]{Staley2017} \pval testing does not provide a route to confirmation.
-This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed''. 
-\jd{Why does Morgan cite Kramer?} \citet{Kramer2011}.
+Even in cases where the null hypothesis is sensible (e.g., particle physics, \cite{Staley2017}), NHST does not provide evidence that a difference is exactly zero.
+This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed'' \citet[cited in \cite{Kramer2011}]{ZiliakandMcCloskey2008}.
 
@@
 In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}. 
-In other cases (e.g., multi-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether something has been seen clearly.
+In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
 
@@
 
-\jd{Not sure how this P. fits in, either. I guess I'd like to keep it, though.}
+Improving language will not by itself solve all of the known problems with current statistical practice.
 We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.

### 2018-10-09 doc.tex
remove redundant abstract title
put table in its own tex. Needs to be uploaded as a separate pdf

@@
 
-  \textbf{Abstract}: Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
+Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
 We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
@@
 
-\newcommand{\ourcomment}[1]{[\emph{#1}]}
-\begin{table}
-\setlength\tabcolsep{1cm}.
-\begin{tabular}{p{7.0cm}p{7.0cm}}
-\textbf{Language from published articles} & \textbf{Rewritten using ``clarity''} \\
-\hline\\
-
-\multicolumn{2}{c}{\emph{\textbf{Accepting the null hypothesis ($\boldsymbol{p > 0.05 \nRightarrow}$ no effect)}}} \\
-\hline
-
-Toxins accumulate after acute exposure but have no effect on behaviour
-& Toxins accumulate after acute exposure but their effects on behaviour are statistically unclear
-\\
-
-\rowcolor{vlg}
-There was no effect of elevated carbon dioxide on reproductive behaviors 
-& The effect of elevated carbon dioxide on reproductive behaviors was statistically unclear
-\\
-
-The finding that species richness showed no significant relationship with the area of available habitat is surprising because richness is usually strongly influenced by landscape context 
-& Although species richness is usually strongly influenced by landscape context, we were unable to find a statistically clear relationship in this study
-\\ \\
-
-\multicolumn{2}{c}{\emph{\textbf{Inferring weak effects from large \pvals}} \citep{WassersteinandLazar2016}}
-\\
-\hline
-%% left ``P values'' unchanged here (not \pvals) since it's a quotation
-\ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
-& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{confidence intervals would also be valuable here!}
-\\ \\
-
-\multicolumn{2}{c}{\emph{\textbf{The difference between ``clear'' and ``not clear'' is not clear}} \citep{GelmanandStern2006}}
-\\
-\hline
-
-This correlation was significant in males ($\rho=0.35$, P \textless 0.05) but not females ($\rho=0.35$, NS).
-\ldots \ourcomment{The authors later write as though they have demonstrated a difference between males and females}
-& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{This phrasing may suggest to the authors that confidence intervals are called for.}
-\\
-\rowcolor{vlg}
-\ldots risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
-(adjusted OR 2.99, 95\% CI 1.33–6.74), but no association was found between HCV coinfection and low BMD in men 
-(adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots 
-The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men remain unclear.
-& 
-\ldots  risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
-(adjusted OR 2.99, 95\% CI 1.33–6.74), but the association between HCV coinfection and low BMD in men was not
-statistically clear (adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots  Pursuing biological differences between women and men in the effect of HIV on BMD would be premature given these results.
-\\
-\end{tabular}
-\captionof{table}{Examples of misleading language in peer-reviewed papers (citations available by request), and revisions using our proposed  language of clarity.}
-\label{quotetab}
-\end{table}
-
 \subsection*{Conclusions}

### 2018-10-09 doc.tex
Some rearrangement:

@@
 
-The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \citealt{Abelson1997} for arguments for NHST \bmb{what's in Abelson?
-How much of our argument do they anticipate?}).
+The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \citealt{Abelson1997} for arguments for NHST).
 The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
@@
 For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows published examples of statements that misinterpret \pvals in three different ways and demonstrates how to rephrase them in the language of clarity.
+
+\clearpage
+
+\input{table.tex}
+
+\clearpage
 

### 2018-10-09 doc.tex
tweak abstract

@@
 Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
-We believe that a significant part of the problem is due simply to language: significance testing has little to do with other meanings of the word ``significance''.
+We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''.
 Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.

### 2018-10-10 doc.tex
Some hacky (meant to be quick) changes in formatting for submission to ecology

@@
-\begin{abstract}
-
-Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
-We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''.
-Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
-whether we can clearly see that a correlation or between-group difference is positive or negative).
-We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than statistical ``significance''.
-This simple semantic change could substantially enhance clarity in statistical communication.
-
-\end{abstract}
-
 \flushbottom
@@
 
-\section*{Introduction}
+\linenumbers
+\doublespacing
 
-Statisticians and scientists have bemoaned the shortcomings of null hypothesis significance testing (NHST) for nearly a century \citep{Cohen1994}.
+\subsection*{Abstract}
+
+\noindent Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
+We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''.
+Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
+whether we can clearly see that a correlation or between-group difference is positive or negative).
+We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than statistical ``significance''.
+This simple semantic change could substantially enhance clarity in statistical communication.
+
+\subsection*{Key Words}
+
+\noindent Statistical philosophy; Statistical clarity; Hypothesis testing; \pval
+
+\clearpage
+
+\subsection*{Introduction}
+
+\noindent Statisticians and scientists have bemoaned the shortcomings of null hypothesis significance testing (NHST) for nearly a century \citep{Cohen1994}.
 Books and articles proposing the de-emphasis or abandonment of the \pval have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
@@
 Other prescriptions have included the complete abandonment of frequentist statistics \citep{The2011}, or the use of a stricter significance threshold (e.g.
-$p < 0.005$: \citealt{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.
+$p < 0.005$: \cite{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.
 
@@
 
-\section*{The null hypothesis is false}
+\subsection*{The null hypothesis is false}
 
-In most biological studies, the null hypothesis is known or believed to not be strictly true.
+\noindent In most biological studies, the null hypothesis is known or believed to not be strictly true.
 Even in cases where the null hypothesis is sensible (e.g., particle physics, \cite{Staley2017}), NHST does not provide evidence that a difference is exactly zero.
@@
 
-\section*{The \pval is a property of the study}
+\subsection*{The \pval is a property of the study}
 
-We often see sentences like, ``X et al.
+\noindent We often see sentences like, ``X et al.
 showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
@@
 
-The statement ``X et al. showed that Y has a statistically significant effect on Z'' is similarly misleading.
+The statement ``X et al.
+showed that Y has a statistically significant effect on Z'' is similarly misleading.
 Frequentist statistics effectively assume that the effect is present (or at least, admit that it can't be disproven).
 The question is whether it is seen in a particular data set.
-The statement ``X et al. were able to see the effect of Y on Z'' is not only more accurate, but it appropriately implies that something is missing: \emph{What} effect did they see?
+The statement ``X et al.
+were able to see the effect of Y on Z'' is not only more accurate, but it appropriately implies that something is missing: \emph{What} effect did they see?
 
-\section*{Statistical Clarity}
+\subsection*{Statistical clarity}
 
-The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \citealt{Abelson1997} for arguments for NHST).
+\noindent The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \cite{Abelson1997} for arguments for NHST).
 The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
@@
 showed that the effect of Y on Z is statistically unclear'', is noticeably awkward.
-It seems less like a statement about the study system, and suggests the more straightforward ``did not find a statistically clear effect.''
-Similarly, ``We did not find a clear difference in response between the control and sham groups'' is both more colloquial and harder to transform into a misleading statement than ``We did not find a significant difference \ldots''.
+It seems less like a statement about the study system, and suggests the more straightforward ``did not find a statistically clear effect.'' Similarly, ``We did not find a clear difference in response between the control and sham groups'' is both more colloquial and harder to transform into a misleading statement than ``We did not find a significant difference \ldots''.
 \citet{Bernardietal.2017} complained that ``\ldots sociological and social significance are sacrificed on the altar of statistical significance''.
@@
 
-\clearpage
-
-\input{table.tex}
-
-\clearpage
-
 \subsection*{Conclusions}
 
-We believe that NHST is useful as a simple, robust way to ask whether an effect can be seen clearly in a particular data set \citep{robinson2001past}, and that careful, clarity-based language can reduce misinterpretation and miscommunication.
+\noindent We believe that NHST is useful as a simple, robust way to ask whether an effect can be seen clearly in a particular data set \citep{robinson2001past}, and that careful, clarity-based language can reduce misinterpretation and miscommunication.
 
@@
 
-We thank members of the Dushoff and Bolker labs for helpful comments on the first draft of the manuscript.
+\noindent We thank members of the Dushoff and Bolker labs for helpful comments on the first draft of the manuscript.

### 2018-10-15 main.tex
Update main.tex
Meeting with BB
Slight progress (for lots of effort)
various tweaks to ms
lots more comments on last section
put table in its own tex. Needs to be uploaded as a separate pdf
Some rearrangement:
Some hacky (meant to be quick) changes in formatting for submission to ecology
avoid PassOptionsToPackage

@@
-\documentclass[12pt, english]{wlpeerj} % Just a convenient template
+%% https://tex.stackexchange.com/questions/238349/error-option-clash-for-package-xcolor
+%% \PassOptionsToPackage{table,dvipsnames}{xcolor}
+\documentclass[12pt, english, dvipsnames, table]{wlpeerj} % Just a convenient template
+\usepackage{xcolor}
+\definecolor{vlg}{rgb}{0.88, 0.88, 0.88}
 \usepackage{palatino}
@@
 \usepackage[comma]{natbib}
-\bibliographystyle{chicago2}
+\bibliographystyle{unsrtnat}
 \usepackage{url}
@@
 \usepackage{afterpage}
-\usepackage[colorlinks=true, citecolor = blue, linkcolor = black]{hyperref}
+\usepackage[colorlinks=true, citecolor = purple, linkcolor = purple]{hyperref}
 \usepackage{environ}
@@
 \usepackage{setspace}
+\usepackage{framed}
 \newcommand{\figref}[1]{Figure~\ref{fig:#1}}
@@
 \singlespacing
+\raggedright
+\parskip 0pt 
+\usepackage{indentfirst}
+\setlength{\parindent}{0.5cm}
 
-\newcommand{\jd}[1]{{\bf \color{blue} JD: #1}}
-\newcommand{\mk}[1]{{\bf \color{red} MK: #1}}
-\newcommand{\bmb}[1]{{\bf \color{green} BMB: #1}}
+%% This whole effort was a disaster!
+%% \usepackage[left=2.0in]{geometry} % For reasonable spacing with todonotes
+% \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+% \newcommand{\note}[2]{{\todo[linecolor=#1,backgroundcolor=#1!25,bordercolor=#1]{#2}{}}}
 
-\title{Is statistical significance a thing?}
+\newcommand{\note}[2]{{\bf \color{#1} #2}}
+\newcommand{\jd}[1]{\note{blue}{JD: #1}}
+\newcommand{\mk}[1]{\note{red}{MK: #1}}
+\newcommand{\bmb}[1]{\note{magenta}{BMB: #1}}
+
+\newcommand{\pval}{p-value\xspace}
+\newcommand{\pvals}{p-values\xspace}
+\newcommand{\citeneeded}{\textbf{CITE}}
+
+\title{I can see clearly now: reinterpreting statistical significance}
 
@@
 \author[1]{Morgan P. Kain}
-\author[1,2]{Ben M. Bolker?}
+\author[1,2]{Benjamin M. Bolker}
 
@@
 
-\newpage
-\singlespacing
+\clearpage
 
@@
 
+\clearpage
+
+\input{table.tex}
+
+\clearpage
+
 \end{document}

### 2018-10-27 table.tex

\newcommand{\ourcomment}[1]{[\emph{#1}]}
\begin{table}
\setlength\tabcolsep{1cm}.
\begin{tabular}{p{7.0cm}p{7.0cm}}
\textbf{Language from published articles} & \textbf{Rewritten using ``clarity''} \\
\hline\\

\multicolumn{2}{c}{\emph{\textbf{Accepting the null hypothesis ($\boldsymbol{p > 0.05 \nRightarrow}$ no effect)}}} \\
\hline

Toxins accumulate after acute exposure but have no effect on behaviour
& Toxins accumulate after acute exposure but their effects on behaviour are statistically unclear
\\

\rowcolor{vlg}
There was no effect of elevated carbon dioxide on reproductive behaviors 
& The effect of elevated carbon dioxide on reproductive behaviors was statistically unclear
\\

The finding that species richness showed no significant relationship with the area of available habitat is surprising because richness is usually strongly influenced by landscape context 
& Although species richness is usually strongly influenced by landscape context, we were unable to find a statistically clear relationship in this study
\\ \\

\multicolumn{2}{c}{\emph{\textbf{Inferring weak effects from large \pvals}} \citep{WassersteinandLazar2016}}
\\
\hline
%% left ``P values'' unchanged here (not \pvals) since it's a quotation
\ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{confidence intervals would also be valuable here!}
\\ \\

\multicolumn{2}{c}{\emph{\textbf{The difference between ``clear'' and ``not clear'' is not clear}} \citep{GelmanandStern2006}}
\\
\hline

This correlation was significant in males ($\rho=0.35$, P \textless 0.05) but not females ($\rho=0.35$, NS). \ldots \ourcomment{The authors later write as though they have demonstrated a difference between males and females}
& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{This phrasing may suggest to the authors that confidence intervals are called for.}
\\
\rowcolor{vlg}
\ldots risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
(adjusted OR 2.99, 95\% CI 1.33–6.74), but no association was found between HCV coinfection and low BMD in men 
(adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots 
The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men remain unclear.
& 
\ldots  risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
(adjusted OR 2.99, 95\% CI 1.33–6.74), but the association between HCV coinfection and low BMD in men was not
statistically clear (adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots  Pursuing biological differences between women and men in the effect of HIV on BMD would be premature given these results.
\\
\end{tabular}
\captionof{table}{Examples of misleading language in peer-reviewed papers (citations available by request), and revisions using our proposed  language of clarity.}
\label{quotetab}
\end{table}

### 2018-11-05 doc.tex
MEE format

@@
 \maketitle
-\newpage
-\thispagestyle{empty}
+%\newpage
+%\thispagestyle{empty}
 
-\clearpage
+%\clearpage
 
 \linenumbers
-\doublespacing
+
+\subsection*{Running Title}
+
+Statistical Clarity
+
+\subsection*{Word Count}
+
+2,220
 
@@
 
-\noindent Null hypothesis significance testing remains popular despite decades of concern about misuse and misinterpretation.
-We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''.
+\begin{enumerate}
+
+\item Null hypothesis significance testing (NHST) remains popular despite decades of concern about misuse and misinterpretation.
+Recent suggestions for mitigating the problems of NHST that continue to plague ecology (and other fields) include calls for abandoning NHST in favor of Bayesian of information-theoretic approaches.
 Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
 whether we can clearly see that a correlation or between-group difference is positive or negative).
+\item We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''.
 We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than statistical ``significance''.
-This simple semantic change could substantially enhance clarity in statistical communication.
+We illustrate our point by rewriting common misinterpretations of the meaning of statistical tests found in the literature using the language of ``clarity''.
+\item The meaning of statistical tests become easier to interpret and explain when viewed through the lens of ``statistical clarity''.
+\item Our suggestion is mild, but practical: this simple semantic change could substantially enhance clarity in statistical communication.
+
+\end{enumerate}
 
@@
 \clearpage
+\doublespacing
 
@@
 
+%\clearpage
+%\input{table.tex}
+%\clearpage
+
 \subsection*{Conclusions}

### 2018-11-06 doc.tex
twiddling structure abstract

@@
 \item Null hypothesis significance testing (NHST) remains popular despite decades of concern about misuse and misinterpretation.
-Recent suggestions for mitigating the problems of NHST that continue to plague ecology (and other fields) include calls for abandoning NHST in favor of Bayesian of information-theoretic approaches.
-Despite the limitations of null-hypothesis tests, we argue here that they remain useful in many contexts as a guide to whether a certain effect can be seen \emph{clearly} in that context (e.g.
+There are many recent suggestions for mitigating problems arising from NHST, including calls for abandoning NHST in favor of Bayesian or information-theoretic approaches.
+We believe that NHST will continue to be widely used, and can be most usefully interpreted as a guide to whether a certain effect can be seen \emph{clearly} in a particular context (e.g.
 whether we can clearly see that a correlation or between-group difference is positive or negative).
-\item We believe that much of the problem is due to language: significance testing has little to do with other meanings of the word ``significance''.
-We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than statistical ``significance''.
+\item We believe that much misinterpretation of NHST is due to language: significance testing has little to do with other meanings of the word ``significance''.
+We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than ``significance''.
 We illustrate our point by rewriting common misinterpretations of the meaning of statistical tests found in the literature using the language of ``clarity''.

### 2019-01-06 doc.tex
Last version with dmu

@@
 
-The value of NHST can be seen in something like a permutation-based t-test \cite[Chapter 1]{GoodBook}: it provides a simple, robust framework to ask whether we can tell \emph{which} mean is bigger.
-More generally, testing the null hypothesis is a proxy for asking whether we clearly see a signal of how our data differs from it.
-In many cases, this comes down simply to whether we can be confident of the \emph{sign} of a difference or a correlation coefficient \citep{robinson2001past}.
-In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
+The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we clearly \emph{how} our data differs from it.
+For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we a confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we can see the sign of the correlation coefficient \citep{robinson2001past}.
+In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
 

### 2019-01-06 rebuttal.md
First crack at revisions (not really done)

Reviewer: 1
===========

_This perspective paper proposes that we change the language we use to report significance of hypothesis tests. They suggest that a simple change in the language will help clarify the meaning and also help highlight the importance of effect sizes and confidence intervals. Overall, it’s well-written and is a good contribution to this important subject area. We should be open to ideas that experiment and potentially improve how we use NHST._

_I agree that a downside of hypothesis testing is often (wrongly) seen as an end in itself, rather than the scientific knowledge that is gained from the test. However, I am not convinced that your suggestion will solve this. Here are my thoughts:_

Thanks for your perspective. We are also not convinced our suggestion will solve this major problem, to put it mildly. But we are hoping it will help (and think that in small ways it already has). We respond to your specific points below.

_2. I don’t understand the logic that using the term ‘clear’ automatically makes the need for effect sizes and confidence intervals more obvious. Can you explain this logical jump more fully within the manuscript?_

We don't argue that it's automatic, but we do rely on the assumption that use of a term whose colloquial meaning closely matches what P values indicate will lead to clearer communication. We have attempted to stress this more clearly in the revised MS. TODO

_3. If some people adopt this terminology, whilst others do not, it could become a very confusing and unclear landscape of scientific understanding. I think this would have more strength if a single domain or several journals gave new guidelines to only use this term, however that would likely require a more evidence-based case than presented here._

We agree, and hope to head in this direction. Publishing the idea is, we hope, a first step. We have found through informal discussion that there is little confusion when the idea of clarity is combined with reference to P values or confidence intervals. We have made this point more explicit in the MS. TODO

_4. The philosophy of NHST is so deeply embedded within science, it seems unlikely that changing the terminology will change how people use or interpret NHST. For example ‘significance’ has a technical and objective meaning. ‘clear’ is a simpler word that is also more subjective. Using ‘clear’ may allow “significant” to reclaim its common definition, but perhaps ‘clear’ would then become a term that has a specific and altered meaning within scientific manuscripts, with all the same drawbacks that ‘significance’ now has. i.e. maybe the benefits would be short-lived until we are familiar with the new term._

Maybe. Both words have subjective meanings, and either word can be vested with a technical statistical meaning. Our larger point is that the technical statistical meaning has more in common with the informal meanings of "clear" than "significant".

_In some of the examples in your table, the sentences on the right are better, but that seems to be unconnected to the use ‘clear’. In 5th example, your phrasing is much improved, but seems that the word ‘clear’ could be replaced with ‘significant’ for the same effect. So this table seems to confound poor interpretation practice with the language used. I recognise that you claim the language will help the interpretation, but it’s difficult to judge that from these examples._

This is a good point, and also a tricky one. The bad wording is from the literature. We believe that confusion arising partially from the poor fit of the word "significant" to this application is leading to poor wording, but there is no easy way to de-confound. We have pointed this out more explicitly now. TODO

_Line 92 “promise to substantially improve statistical communication”. This is a bold and unsubstantiated claim!_

We have toned down the claim. TODO

Reviewer: 2
===========

_I really liked this piece! I have frequently been frustrated with the interpretation of p-values among my colleagues (and by myself, at different stages in the past) and so i welcome the clarity that you are trying to bring to this important point._

_As a brief summary of the paper's argument: the frequent misinterpretation of NHST is due to confusing language around the results of tests. The suggestion is that we switch to considering p-values as a measure of "clarity" : that is, how clearly an effect could be seen. This language is narrower by design: too narrow, in fact, to cover all the meanings we might want to extract from a statistical procedure. The hope then is that scientists would move on to describe exactly *what* was detected clearly: an effect size, a point estimate and confidence interval, etc._

_I was confused by the paragraph starting on Line 55. A "permutation-based t-test" is a very specific metaphor, and I don't think that readers will grasp the similarity to the p-values from, say, an ANOVA without a bit more signposting.  More generally, I expected this paragraph to summarize the "correct" interpretation of p-values, and perhaps to illustrate how and why they are used in scientific papers._

_My major concern from the beginning of this manuscript is actually mentioned by the authors themselves towards the end: the so-called "Winner's Curse". This is the idea, articulated by Andrew Gelman among others, that if an effect is "significant" it is also likely to be an overestimate. In low-powered studies, the estimated effect size can even be opposite in direction to the true effect, yet the p-value is still a low number.  Many ecologists (in my experience) believe that a low p-value indicates two things at the same time: first, that the study "worked"; second, that the effect is real. Neither is necessarily true, and neither can be reliably inferred from the p-value alone. I'm sure the authors are aware of these points, and i think it would be useful to expand on them a bit more. In brief, while I really like the idea of "seeing with clarity", i would appreciate some discussion of how to tell if one has clearly seen a mere mirage._

This is an important concern. We have expanded our discussion of this point, while trying not to stray too far from our main focus.

_I really enjoyed this manuscript and i think ecologists need to read it. I don't want to be negative, but I can't resist a skeptical question: is there any evidence that people will change their behaviours? Misinterpretation of p-values is but one of the many statistical and philosophical errors that pervade science. These will persist until incentive structures change. Until they do, people will continue to abuse their data, their analyses, and their interpretations._

We agree that this article will not change much, but we hope it will be part of a larger change in a good direction.

### 2019-01-06 doc.tex
First crack at revisions (not really done)

@@
 \item The meaning of statistical tests become easier to interpret and explain when viewed through the lens of ``statistical clarity''.
-\item Our suggestion is mild, but practical: this simple semantic change could substantially enhance clarity in statistical communication.
+\item Our suggestion is mild, but practical: this simple semantic change could enhance clarity in statistical communication.
 
@@
 This is a step in the right direction.
-Replacing ``significance'' with ``clarity'' takes this idea further, and has the promise to substantially improve statistical communication.
+Replacing ``significance'' with ``clarity'' takes this idea further, and has the potential to improve statistical communication.
 
@@
 For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows published examples of statements that misinterpret \pvals in three different ways and demonstrates how to rephrase them in the language of clarity.
+We have attempted to do this thoughtfully, and therefore the language on the right differs from the language on the left in many ways.
+The point is not that changing ``significance'' to ``clarity'' is a substantial improvement by itself, but that it can prompt rethinking and reinterpretation.
 
-%\clearpage
-%\input{table.tex}
-%\clearpage
+\subsection*{Caveats}
+
+The suggested change in language should help focus attention on improved statistical practice, but does not guarantee it.
+In particular, there is a danger that ``statistical clarity'' will eventually come to be seen as end to itself, the way that ``significance'' is now.
+The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, not the system, and of focusing on effects.
+
+The use of statistical clarity could be confounded with other meanings of the word clarity.
+We have found that scientists' understand of our proposed use of statistical clarity is enhanced by connecting clarity statments to statements about P values.
+
+ADD a bit about winners' curses, plausibility and the like here (and take some of it out of the Conclusions.
 

### 2019-01-07 rebuttal.md
Flesh out rebuttal before pinging people
First pass at revisions and rebuttal

@@
 We don't argue that it's automatic, but we do rely on the assumption that use of a term whose colloquial meaning closely matches what P values indicate will lead to clearer communication.
-We have attempted to stress this more clearly in the revised MS.
-TODO
+We gave an example where we believe the word "clear" underlines the absence of effect sizes (L136 of ORIGINAL), and mentioned CIs in the table.
+We have now added another mention to the table, and an UNCONVINCING comment to the ¶ where we present the table.
 
@@
 
-We agree, and hope to head in this direction.
+We agree about strength, and hope to head in this direction.
 Publishing the idea is, we hope, a first step.
@@
 We have made this point more explicit in the MS.
-TODO
 
@@
 We have pointed this out more explicitly now.
-TODO
 
@@
 
-We have toned down the claim. TODO
+We have toned down the claim.
 
@@
 More generally, I expected this paragraph to summarize the "correct" interpretation of p-values, and perhaps to illustrate how and why they are used in scientific papers._
+
+We have rewritten the paragraph to be more straightforward.
 
@@
 
-We agree that this article will not change much, but we hope it will be part of a larger change in a good direction.
+Thanks for your kind words. We agree that this article will not change much, but we hope it will be part of a larger change in a good direction.

### 2019-01-07 doc.tex
First pass at revisions and rebuttal

@@
 
-The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we clearly \emph{how} our data differs from it.
-For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we a confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we can see the sign of the correlation coefficient \citep{robinson2001past}.
-In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, accepted way to evaluate whether an effect has been seen clearly.
+The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
+For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
+In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, widely accepted way to evaluate whether an effect has been seen clearly.
 
@@
 The point is not that changing ``significance'' to ``clarity'' is a substantial improvement by itself, but that it can prompt rethinking and reinterpretation.
+We also hope that, by drawing attention to effects, the language of clarity will encourage more reporting of effect sizes and confidence intervals.
 
@@
 The use of statistical clarity could be confounded with other meanings of the word clarity.
-We have found that scientists' understand of our proposed use of statistical clarity is enhanced by connecting clarity statments to statements about P values.
+We have found that scientists' understanding of our proposed use of statistical clarity is enhanced by explicitly connecting clarity statments to statements about P values.
 
 ADD a bit about winners' curses, plausibility and the like here (and take some of it out of the Conclusions.
+Should we say specifically that we are agnostic about (supportive of?) the idea that NHST and/or frequentist stats are overused?
 

### 2019-01-07 table.tex
Cleaning

@@
 \ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
-& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{confidence intervals would also be valuable here!}
+& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{since smallness is no longer implied the authors might now think of adding confidence intervals.}
 \\ \\
@@
 \ldots \ourcomment{The authors later write as though they have demonstrated a difference between males and females}
-& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{This phrasing may suggest to the authors that confidence intervals are called for.}
+& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{Again, this phrasing may suggest to the authors that confidence intervals are called for.}
 \\

### 2019-01-07 table.tex
Annotating invisible changes

--- 2018-10-27 table.tex
@@
 \ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
-& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{confidence intervals would also be valuable here!}
+& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{since smallness is no longer implied the authors might now think of adding confidence intervals.
+\jd{Changed.}}
 \\ \\
@@
 \ldots \ourcomment{The authors later write as though they have demonstrated a difference between males and females}
-& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{This phrasing may suggest to the authors that confidence intervals are called for.}
+& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{Again, this phrasing may suggest to the authors that confidence intervals are called for.
+\jd{Changed slightly, should we also consider changing the order of these two?}}
 \\

### 2019-01-07 rebuttal.md
BMB general messing around

@@
 We are also not convinced our suggestion will solve this major problem, to put it mildly.
-But we are hoping it will help (and think that in small ways it already has).
+But we hope it will help (and think that in small ways it already has).
 We respond to your specific points below.
@@
 
-Thanks for your kind words. We agree that this article will not change much, but we hope it will be part of a larger change in a good direction.
+Thanks for your kind words. We agree that this article cannot by itself overcome deeply embedded bad practice, but we hope it will be part of a larger change in a good direction.

### 2019-01-07 doc.tex
BMB general messing around

@@
 
-\noindent In most biological studies, the null hypothesis is known or believed to not be strictly true.
+\noindent In most biological studies, the null hypothesis is known \emph{a priori} to be false.
 Even in cases where the null hypothesis is sensible (e.g., particle physics, \cite{Staley2017}), NHST does not provide evidence that a difference is exactly zero.
@@
 The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
-For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
+For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger} (and whether the size of the difference is biologically interesting); similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
 In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, widely accepted way to evaluate whether an effect has been seen clearly.
@@
 The ``idiocy'', if any, comes in the interpretive step.
-A statistical fact (``we have \emph{seen} a difference between the groups'', which should immediately prompt the question ``what have you learned \emph{about} that difference?'') is interpreted as a scientific fact (``there \emph{is} a `significant' difference between the groups), which is often seen as an end in itself: ``we showed that the groups differ''.
+A statistical fact (``we have \emph{seen} a difference between the groups'', which should immediately prompt the question ``what have you learned \emph{about} that difference?'') is interpreted as a scientific fact (``there \emph{is} a `significant' difference between the groups''), which is often seen as an end in itself: ``we showed that the groups differ''.
 
@@
 
-\noindent We often see sentences like, ``X et al.
+\noindent Researchers often write sentences like, ``X et al.
 showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
@@
 For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows published examples of statements that misinterpret \pvals in three different ways and demonstrates how to rephrase them in the language of clarity.
-We have attempted to do this thoughtfully, and therefore the language on the right differs from the language on the left in many ways.
-The point is not that changing ``significance'' to ``clarity'' is a substantial improvement by itself, but that it can prompt rethinking and reinterpretation.
+We have attempted to do this thoughtfully, and therefore the language on the right differs from the language on the left by more than a simple substitution of ``significance'' to ``clarity''.
+We do not claim that executing a search-and-replace operation will automatically improve statistical practice; rather, we think it can prompt rethinking and reinterpretation.
 We also hope that, by drawing attention to effects, the language of clarity will encourage more reporting of effect sizes and confidence intervals.
@@
 
-The suggested change in language should help focus attention on improved statistical practice, but does not guarantee it.
-In particular, there is a danger that ``statistical clarity'' will eventually come to be seen as end to itself, the way that ``significance'' is now.
-The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, not the system, and of focusing on effects.
-
-The use of statistical clarity could be confounded with other meanings of the word clarity.
-We have found that scientists' understanding of our proposed use of statistical clarity is enhanced by explicitly connecting clarity statments to statements about P values.
-
-ADD a bit about winners' curses, plausibility and the like here (and take some of it out of the Conclusions.
-Should we say specifically that we are agnostic about (supportive of?) the idea that NHST and/or frequentist stats are overused?
+Changing from ``significance'' to ``clarity'' should help researchers improve their statistical practice, but of course it cannot solve all of our problems with statistics.
+\bmb{repetitive with \P 3 of Conclusion?}The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals.
+If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now; similarly, ``statistical clarity'' could be confounded with other meanings of  ``clarity'' as ``significance'' is now.
+We hope not, but in any case we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''.
+We have found that scientists' understanding of our proposed use of statistical clarity is enhanced by explicitly connecting clarity statements to statements about P values.
 
@@
 We agree with \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}, that scientific communication and understanding will be improved by a shift away from \pvals to effect sizes and confidence intervals.
-We argue that the use of ``statistical clarity'' reinforces the need for confidence intervals and effect sizes by making it clearer that bald statements about \pvals are insufficient.
+The use of ``statistical clarity'' should reinforce the need for confidence intervals and effect sizes by making bald statements about \pvals more obviously insufficient.
 The statement ``The difference between our control and treatment groups was not statistically clear ($p = 0.30$)'' is noticeably incomplete; an effect size and confidence interval are required to complete the story.
@@
 Improving language will not by itself solve all of the known problems with current statistical practice.
-We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanism, study design and data quality, real world benefits, novelty and other factors) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
-Additionally, we support the idea of writing a statistical journal that chronicles all steps in the analytical process \citep{Kassetal.2016}, and clearly delineating the boundary between inferences based on \emph{a priori} hypotheses and discoveries from \emph{post hoc} data exploration.
+We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanisms, study design and data quality, real world benefits, novelty, etc.) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
+Additionally, we support the writing of statistical journals that chronicle all of the steps in the analytical process \citep{Kassetal.2016}, and clearly delineating the boundary between inferences based on \emph{a priori} hypotheses and discoveries from \emph{post hoc} data exploration.
+These procedures help to avoid the ``garden of forking paths'' by which cryptic multiple testing amplifies noise to make it look like a signal of biologically interesting processes \citep{gelman_statistical_2014}).
 

### 2019-01-09 doc.tex
Fiddling a bit.

@@
 The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
-For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger} (and whether the size of the difference is biologically interesting); similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
+For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
 In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, widely accepted way to evaluate whether an effect has been seen clearly.

### 2019-01-09 doc.tex
A bit more fiddling; I would like to hand off.

@@
 Changing from ``significance'' to ``clarity'' should help researchers improve their statistical practice, but of course it cannot solve all of our problems with statistics.
-\bmb{repetitive with \P 3 of Conclusion?}The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals.
-If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now; similarly, ``statistical clarity'' could be confounded with other meanings of  ``clarity'' as ``significance'' is now.
-We hope not, but in any case we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''.
-We have found that scientists' understanding of our proposed use of statistical clarity is enhanced by explicitly connecting clarity statements to statements about P values.
+\bmb{repetitive with \P 3 of Conclusion?} The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals.
+If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now.
+We hope not, but in we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''.
+If there is a transition it will also be important to communicate clearly when ``clarity'' is being used in a technical sense; we have found that in particular that understanding is improved by explicitly connecting clarity statements to statements about P values.
 

### 2019-01-09 eggplant.R
In class with Bolker

@@ -1,0 +1,1 @@
+x <- 3+2				

### 2019-01-13 doc.tex
few comments by MK

@@
 
-The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
+The value of NHST is that \mk{Maybe just begin this sentence with ``Asking''?
+I still don't really like how this sentence sounds} asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
 For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
@@
 In fact, the sentence is erroneous even before we get to the implication: significance tests provide information about \emph{a data set} -- that is, about a study, not about the study system \citep{HoenigandHeisey2001}.
-Indeed, a very small effect can lead to $p < 0.05$, when data is abundant (or noise is small); or a very large one can lead to $p > 0.05$ when the sample is small or noisy.
+Indeed, a very small effect can lead to $p < 0.05$, \mk{remove Indeed and both commas in this sentence (semi-colon becomes a comma)?} when data is abundant (or noise is small); or a very large one can lead to $p > 0.05$ when the sample is small or noisy.
 
@@
 showed that Y has a statistically significant effect on Z'' is similarly misleading.
-Frequentist statistics effectively assume that the effect is present (or at least, admit that it can't be disproven).
+Frequentist statistics effectively assume that the effect is present (or at least, \mk{no comma needed here?} admit that it can't be disproven).
 The question is whether it is seen in a particular data set.
@@
 
-\noindent The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \cite{Abelson1997} for arguments for NHST).
+\noindent The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \cite{Abelson1997} for arguments for NHST) \mk{Is there a better place to cite this (maybe in the last sentence of the intro)?}.
 The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
@@
 Changing from ``significance'' to ``clarity'' should help researchers improve their statistical practice, but of course it cannot solve all of our problems with statistics.
-\bmb{repetitive with \P 3 of Conclusion?} The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals.
+\bmb{repetitive with \P 3 of Conclusion?} \mk{Maybe not needed here at all considering that this second sentence doesn't even directly follow.
+I vote to just remove this first sentence} The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals.
 If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now.

### 2019-01-13 rebuttal.md
Fiddling a bit.
Add BB suggested comment
single comment to rebuttal

@@
+BB thinks we should have a preamble about how we're not solving the world's problems.
+JD is not so sure (especially since the first response tends in that direction already).
+MK: We need a short cover letter in addition to this document correct?
+Put a brief statement about this there?
+
 Reviewer: 1
@@
 Our larger point is that the technical statistical meaning has more in common with the informal meanings of "clear" than "significant".
+We now make the point that caution is required in this regard.
 

### 2019-01-15 doc.tex
Going through MK's comments

--- 2019-01-09 doc.tex
@@
 
-Here, we argue that NHST remains useful, and that pervasive misuse can be reduced through a linguistic change: using the language of statistical ``clarity'' instead of statistical ``significance''.
+We believe that NHST can be useful as a simple criterion for evaluating whether a data signal is clear  (see \cite{Abelson1997} for arguments for NHST), and that pervasive misuse can be reduced through a linguistic change: using the language of statistical ``clarity'' instead of statistical ``significance''.
 
@@
 
-The value of NHST is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
+Part of the answer is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
 For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
@@
 In fact, the sentence is erroneous even before we get to the implication: significance tests provide information about \emph{a data set} -- that is, about a study, not about the study system \citep{HoenigandHeisey2001}.
-Indeed, a very small effect can lead to $p < 0.05$, when data is abundant (or noise is small); or a very large one can lead to $p > 0.05$ when the sample is small or noisy.
+A very small effect can lead to $p < 0.05$ when data is abundant (or noise is small); or a very large one can lead to $p > 0.05$ when the sample is small or noisy.
 
@@
 showed that Y has a statistically significant effect on Z'' is similarly misleading.
-Frequentist statistics effectively assume that the effect is present (or at least, admit that it can't be disproven).
+Frequentist statistics effectively assume that the effect is present (or at least admit that it can't be disproven).
 The question is whether it is seen in a particular data set.
@@
 
-\noindent The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \cite{Abelson1997} for arguments for NHST).
+\noindent The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear.
 The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
@@
 
-Changing from ``significance'' to ``clarity'' should help researchers improve their statistical practice, but of course it cannot solve all of our problems with statistics.
-\bmb{repetitive with \P 3 of Conclusion?} The idea of ``statistical clarity'' will work best if it remains linked to the principles of attaching clarity to the study, rather than the system, and of focusing on effects and confidence intervals.
 If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now.
-We hope not, but in we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''.
+We hope this can be avoided, but in any event we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''.
 If there is a transition it will also be important to communicate clearly when ``clarity'' is being used in a technical sense; we have found that in particular that understanding is improved by explicitly connecting clarity statements to statements about P values.

### 2019-01-15 rebuttal.md
Working on rebuttal a bit
Ready to send?

@@
 We don't argue that it's automatic, but we do rely on the assumption that use of a term whose colloquial meaning closely matches what P values indicate will lead to clearer communication.
-We gave an example where we believe the word "clear" underlines the absence of effect sizes (L136 of ORIGINAL), and mentioned CIs in the table.
-We have now added another mention to the table, and an UNCONVINCING comment to the ¶ where we present the table.
+We gave an example where we believe the word "clear" underlines the absence of effect sizes (L80), and mentioned CIs in the table.
+We have now added another mention to the table, and a comment to the ¶ where we present the table.
 

### 2019-01-16 rebuttal.md
bb rebuttal wordsmithing

@@
 
-We don't argue that it's automatic, but we do rely on the assumption that use of a term whose colloquial meaning closely matches what P values indicate will lead to clearer communication.
+We don't argue that it's automatic, but we do rely on the idea that use of a term whose colloquial meaning closely matches what P values indicate will lead to clearer communication.
 We gave an example where we believe the word "clear" underlines the absence of effect sizes (L80), and mentioned CIs in the table.
@@
 
-We agree about strength, and hope to head in this direction.
+We agree about that these practices would be stronger if they were institutionalized, and hope to head in this direction.
 Publishing the idea is, we hope, a first step.
-We have found through informal discussion that there is little confusion when the idea of clarity is combined with reference to P values or confidence intervals.
+We have found through informal discussion that there is little confusion when our recommended *qualitative* statements about statistical clarity are combined with *quantitative* information about p-values or confidence intervals.
 We have made this point more explicit in the MS.

### 2019-01-23 main.tex
editing style for ArXiv
MEE format
First crack at revisions (not really done)
First pass at revisions and rebuttal
A bit more fiddling; I would like to hand off.
Last bit of clean up before resubmission
Moved material into main.tex, changed style file name

@@
 %% \PassOptionsToPackage{table,dvipsnames}{xcolor}
-\documentclass[12pt, english, dvipsnames, table]{wlpeerj} % Just a convenient template
+\documentclass[12pt, english, dvipsnames, table]{OverleafPJ} % Just a convenient template
 \usepackage{xcolor}
@@
 \usepackage[comma]{natbib}
-\bibliographystyle{unsrtnat}
+\bibliographystyle{chicago2}
 \usepackage{url}
@@
 \newcommand{\note}[2]{{\bf \color{#1} #2}}
-\newcommand{\jd}[1]{\note{blue}{JD: #1}}
-\newcommand{\mk}[1]{\note{red}{MK: #1}}
-\newcommand{\bmb}[1]{\note{magenta}{BMB: #1}}
+\newcommand{\jd}[1]{\note{blue}{[[JD: #1]]}}
+\newcommand{\mk}[1]{\note{red}{[[MK: #1]]}}
+\newcommand{\bmb}[1]{\note{magenta}{[[BMB: #1]]}}
 
@@
 
+%\input{ldpre.tex}
+
 \begin{document}
 
-\input{doc.tex}
+\flushbottom
+\maketitle
+%\newpage
+%\thispagestyle{empty}
+
+%\clearpage
+
+\linenumbers
+
+\subsection*{Running Title}
+
+Statistical Clarity
+
+\subsection*{Word Count}
+
+2,260
+
+\subsection*{Abstract}
+
+\begin{enumerate}
+
+\item Null hypothesis significance testing (NHST) remains popular despite decades of concern about misuse and misinterpretation.
+There are many recent suggestions for mitigating problems arising from NHST, including calls for abandoning NHST in favor of Bayesian or information-theoretic approaches.
+We believe that NHST will continue to be widely used, and can be most usefully interpreted as a guide to whether a certain effect can be seen \emph{clearly} in a particular context (e.g.
+whether we can clearly see that a correlation or between-group difference is positive or negative).
+\item We believe that much misinterpretation of NHST is due to language: significance testing has little to do with other meanings of the word ``significance''.
+We therefore suggest that researchers describe the conclusions of null-hypothesis tests in terms of statistical ``clarity'' rather than ``significance''.
+We illustrate our point by rewriting common misinterpretations of the meaning of statistical tests found in the literature using the language of ``clarity''.
+\item The meaning of statistical tests become easier to interpret and explain when viewed through the lens of ``statistical clarity''.
+\item Our suggestion is mild, but practical: this simple semantic change could enhance clarity in statistical communication.
+
+\end{enumerate}
+
+\subsection*{Key Words}
+
+\noindent Statistical philosophy; Statistical clarity; Hypothesis testing; \pval
+
+\clearpage
+\doublespacing
+
+\subsection*{Introduction}
+
+\noindent Statisticians and scientists have bemoaned the shortcomings of null hypothesis significance testing (NHST) for nearly a century \citep{Cohen1994}.
+Books and articles proposing the de-emphasis or abandonment of the \pval have been cited thousands of times \citep{Cohen1994, Goodman1999, Wilkinson1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}.
+These works plead for a focus on effect sizes and confidence intervals, and point out that null effects that truly have zero magnitude are unrealistic or impossible in most fields outside of the hard physical sciences \citep{Meehl1990, Tukey1991, Cohen1994}.
+Yet, \pvals without confidence intervals (or even effect sizes) and references to null effects still pervade the scientific literature at all levels up to and including articles in high-impact journals.
+
+In a meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report a comprehensible effect size.
+The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
+Other prescriptions have included the complete abandonment of frequentist statistics \citep{The2011}, or the use of a stricter significance threshold (e.g.
+$p < 0.005$: \cite{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.
+
+We believe that NHST can be useful as a simple criterion for evaluating whether a data signal is clear  (see \cite{Abelson1997} for arguments for NHST), and that pervasive misuse can be reduced through a linguistic change: using the language of statistical ``clarity'' instead of statistical ``significance''.
+
+\subsection*{The null hypothesis is false}
+
+\noindent In most biological studies, the null hypothesis is known \emph{a priori} to be false.
+Even in cases where the null hypothesis is sensible (e.g., particle physics, \cite{Staley2017}), NHST does not provide evidence that a difference is exactly zero.
+This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed'' \citet[cited in \cite{Kramer2011}]{ZiliakandMcCloskey2008}.
+
+Part of the answer is that asking whether we can reject the null hypothesis is a proxy for asking whether we see clearly \emph{how} our data differs from it.
+For example, in a t-test, we are nominally asking whether we can see a \emph{difference} between two means, but the scientific question is whether we are confident which of the two means is \emph{larger}; similarly, tests for whether two values are correlated are a proxy for whether we are confident about the \emph{sign} of the correlation coefficient \citep{robinson2001past}.
+In other cases (e.g., a one-way ANOVA), it may not be simple to describe the difference we see, but NHST is still a reasonable, widely accepted way to evaluate whether an effect has been seen clearly.
+
+The ``idiocy'', if any, comes in the interpretive step.
+A statistical fact (``we have \emph{seen} a difference between the groups'', which should immediately prompt the question ``what have you learned \emph{about} that difference?'') is interpreted as a scientific fact (``there \emph{is} a `significant' difference between the groups''), which is often seen as an end in itself: ``we showed that the groups differ''.
+
+\subsection*{The \pval is a property of the study}
+
+\noindent Researchers often write sentences like, ``X et al.
+showed that there is no significant effect of Y on Z'' with the implication that this effect can now be assumed to be absent (or unimportant).
+In fact, the sentence is erroneous even before we get to the implication: significance tests provide information about \emph{a data set} -- that is, about a study, not about the study system \citep{HoenigandHeisey2001}.
+A very small effect can lead to $p < 0.05$ when data is abundant (or noise is small); or a very large one can lead to $p > 0.05$ when the sample is small or noisy.
+
+The statement ``X et al.
+showed that Y has a statistically significant effect on Z'' is similarly misleading.
+Frequentist statistics effectively assume that the effect is present (or at least admit that it can't be disproven).
+The question is whether it is seen in a particular data set.
+The statement ``X et al.
+were able to see the effect of Y on Z'' is not only more accurate, but it appropriately implies that something is missing: \emph{What} effect did they see?
+
+\subsection*{Statistical clarity}
+
+\noindent The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear.
+The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant.
+``Clarity,'' on the other hand, is an apt term for what NHST actually evaluates.
+\citet{jones2000sensible} and \citet{robinson2001past} suggest that researchers should report $p > 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''.
+This is a step in the right direction.
+Replacing ``significance'' with ``clarity'' takes this idea further, and has the potential to improve statistical communication.
+
+For example, the sentence ``X et al.
+showed that the effect of Y on Z is statistically unclear'', is noticeably awkward.
+It seems less like a statement about the study system, and suggests the more straightforward ``did not find a statistically clear effect.'' Similarly, ``We did not find a clear difference in response between the control and sham groups'' is both more colloquial and harder to transform into a misleading statement than ``We did not find a significant difference \ldots''.
+\citet{Bernardietal.2017} complained that ``\ldots sociological and social significance are sacrificed on the altar of statistical significance''.
+Describing statistical tests in terms of clarity would allow ``significant'' to reclaim its common English definition and reduce conflation between statistical results and substantive significance.
+
+Descriptions of statistical results using the language of clarity should begin with reference to the effect.
+For example, ``The difference between the control and treatment group was not statistically clear.'' Table~\ref{quotetab} shows published examples of statements that misinterpret \pvals in three different ways and demonstrates how to rephrase them in the language of clarity.
+We have attempted to do this thoughtfully, and therefore the language on the right differs from the language on the left by more than a simple substitution of ``significance'' to ``clarity''.
+We do not claim that executing a search-and-replace operation will automatically improve statistical practice; rather, we think it can prompt rethinking and reinterpretation.
+We also hope that, by drawing attention to effects, the language of clarity will encourage more reporting of effect sizes and confidence intervals.
+
+\subsection*{Caveats}
+
+If widely adopted, ``statistical clarity'' could eventually come to be seen as an end in itself, the way that ``significance'' is now.
+We hope this can be avoided, but in any event we feel that the unthinking use of ``clarity'' would be (marginally) better than the current unthinking use of ``significance''.
+If there is a transition it will also be important to communicate clearly when ``clarity'' is being used in a technical sense; we have found that in particular that understanding is improved by explicitly connecting clarity statements to statements about P values.
+
+\subsection*{Conclusions}
+
+\noindent We believe that NHST is useful as a simple, robust way to ask whether an effect can be seen clearly in a particular data set \citep{robinson2001past}, and that careful, clarity-based language can reduce misinterpretation and miscommunication.
+
+We agree with \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016}, that scientific communication and understanding will be improved by a shift away from \pvals to effect sizes and confidence intervals.
+The use of ``statistical clarity'' should reinforce the need for confidence intervals and effect sizes by making bald statements about \pvals more obviously insufficient.
+The statement ``The difference between our control and treatment groups was not statistically clear ($p = 0.30$)'' is noticeably incomplete; an effect size and confidence interval are required to complete the story.
+
+Improving language will not by itself solve all of the known problems with current statistical practice.
+We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanisms, study design and data quality, real world benefits, novelty, etc.) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
+Additionally, we support the writing of statistical journals that chronicle all of the steps in the analytical process \citep{Kassetal.2016}, and clearly delineating the boundary between inferences based on \emph{a priori} hypotheses and discoveries from \emph{post hoc} data exploration.
+These procedures help to avoid the ``garden of forking paths'' by which cryptic multiple testing amplifies noise to make it look like a signal of biologically interesting processes \citep{gelman_statistical_2014}).
+
+Whether or not our recommendations are broadly adopted by authors, reviewers, and editors, they can be useful for individual researchers who want to help themselves think clearly about NHST results.
+We have found that rephrasing NHST statements that we encounter (in the literature, or in seminar presentations) in terms of clarity has already helped us with both interpretation and communication.
+
+\subsection*{Acknowledgments}
+
+\noindent We thank members of the Dushoff and Bolker labs for helpful comments on the first draft of the manuscript.
+JD thanks Stellenbosch University's DST-NRF Centre of Excellence in Epidemiological Modelling and Analysis (SACEMA) for support in developing these ideas.
+
+\subsection*{Author contributions}
+
+\noindent JD conceived the main idea of the paper.
+All authors helped to develop it.
+JD and MPK outlined the MS.
+MPK led the literature review and wrote the first draft.
+All authors wrote and revised later drafts.
+
+\subsection*{Data accessibility}
+
+\noindent No data was used in the production of this manuscript.
 
@@
 
-\clearpage
+%\clearpage
 
-\input{table.tex}
+\newcommand{\ourcomment}[1]{[\emph{#1}]}
+\begin{table}
+\setlength\tabcolsep{1cm}.
+\begin{tabular}{p{7.0cm}p{7.0cm}}
+\textbf{Language from published articles} & \textbf{Rewritten using ``clarity''} \\
+\hline\\
 
-\clearpage
+\multicolumn{2}{c}{\emph{\textbf{Accepting the null hypothesis ($\boldsymbol{p > 0.05 \nRightarrow}$ no effect)}}} \\
+\hline
+
+Toxins accumulate after acute exposure but have no effect on behaviour
+& Toxins accumulate after acute exposure but their effects on behaviour are statistically unclear
+\\
+
+\rowcolor{vlg}
+There was no effect of elevated carbon dioxide on reproductive behaviors 
+& The effect of elevated carbon dioxide on reproductive behaviors was statistically unclear
+\\
+
+The finding that species richness showed no significant relationship with the area of available habitat is surprising because richness is usually strongly influenced by landscape context 
+& Although species richness is usually strongly influenced by landscape context, we were unable to find a statistically clear relationship in this study
+\\ \\
+
+\multicolumn{2}{c}{\emph{\textbf{Inferring weak effects from large \pvals}} \citep{WassersteinandLazar2016}}
+\\
+\hline
+%% left ``P values'' unchanged here (not \pvals) since it's a quotation
+\ldots\ differences between treatment and control groups were nonsignificant, with P values of at least 0.3, and most in the range $0.7 \leq P \leq 0.9$.
+& \ldots\ differences between treatment and control groups were not statistically clear (all $P > 0.05$) \ourcomment{since smallness is no longer implied the authors might now think of adding confidence intervals.}
+\\ \\
+
+\multicolumn{2}{c}{\emph{\textbf{The difference between ``clear'' and ``not clear'' is not clear}} \citep{GelmanandStern2006}}
+\\
+\hline
+
+This correlation was significant in males ($\rho=0.35$, P \textless 0.05) but not females ($\rho=0.35$, NS).
+\ldots \ourcomment{The authors later write as though they have demonstrated a difference between males and females}
+& Although males and females show the same correlation coefficient ($\rho=0.35$), the sign of the coefficient is statistically clear only in males  \ldots \ourcomment{Again, this phrasing may suggest to the authors that confidence intervals are called for.}
+\\
+\rowcolor{vlg}
+\ldots risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
+(adjusted OR 2.99, 95\% CI 1.33–6.74), but no association was found between HCV coinfection and low BMD in men 
+(adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots 
+The precise mechanisms for the association between viral hepatitis and low BMD in HIV-infected women but not men remain unclear.
+& 
+\ldots  risk of low BMD [bone mineral density] remained greater in HCV-coinfected women versus women with HIV alone
+(adjusted OR 2.99, 95\% CI 1.33–6.74), but the association between HCV coinfection and low BMD in men was not
+statistically clear (adjusted OR 1.26, 95\% CI 0.75–2.10). \ldots  Pursuing biological differences between women and men in the effect of HIV on BMD would be premature given these results.
+\\
+\end{tabular}
+\captionof{table}{Examples of misleading language in peer-reviewed papers (citations available by request), and revisions using our proposed  language of clarity.}
+\label{quotetab}
+\end{table}
 

### 2019-01-24 main.tex
Lose overleaf template

@@
 %% \PassOptionsToPackage{table,dvipsnames}{xcolor}
-\documentclass[12pt, english, dvipsnames, table]{OverleafPJ} % Just a convenient template
+\documentclass[12pt, english, dvipsnames, table]{article} % Just a convenient template
 \usepackage{xcolor}
@@
 
-\title{I can see clearly now: reinterpreting statistical significance}
-
-\author[1]{Jonathan Dushoff}
-\author[1]{Morgan P. Kain}
-\author[1,2]{Benjamin M. Bolker}
-
-\affil[1]{Department of Biology, McMaster University, 1280 Main Street West, Hamilton, Ontario L8S 4K1 Canada}
-\affil[2]{Department of Mathematics and Statistics, McMaster University, 1280 Main Street West, Hamilton, Ontario 
-L8S 4L8 Canada}
-
-\corrauthor[1]{Jonathan Dushoff}{dushoff@mcmaster.ca}
+\begin{document}
 
@@
 
-\begin{document}
+\section*{I can see clearly now: reinterpreting statistical significance}
+
+\noindent {Jonathan Dushoff}$\mbox{}^{1,*}$
+\hfill
+{Morgan P. Kain}$\mbox{}^{1,*}$
+\hfill
+{Benjamin M. Bolker}$\mbox{}^{1,2}$
+
+\medskip\noindent 1.~{Department of Biology, McMaster University, 1280 Main Street West, Hamilton, Ontario L8S 4K1 Canada}
+
+\medskip\noindent 2.~{Department of Mathematics and Statistics, McMaster University, 1280 Main Street West, Hamilton, Ontario 
+L8S 4L8 Canada}
+
+\medskip\noindent * Corresponding author \tt{dushoff@mcmaster.ca}
 
 \flushbottom
-\maketitle
+%% \maketitle
 %\newpage
@@
 \end{tabular}
-\captionof{table}{Examples of misleading language in peer-reviewed papers (citations available by request), and revisions using our proposed  language of clarity.}
+\caption{Examples of misleading language in peer-reviewed papers (citations available by request), and revisions using our proposed  language of clarity.}
 \label{quotetab}

### 2019-02-10 doc.tex
Last bit of clean up before resubmission
Trying to sort proofs

@@
 
-2,220
+2,260
 
@@
 In a meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report a comprehensible effect size.
-The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use.
+The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneArxiv} its use.
 Other prescriptions have included the complete abandonment of frequentist statistics \citep{The2011}, or the use of a stricter significance threshold (e.g.
@@
 Improving language will not by itself solve all of the known problems with current statistical practice.
-We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanisms, study design and data quality, real world benefits, novelty, etc.) \citep{McShaneetal.2017} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
+We echo previous statements in favor of ``neglected factors'' (prior and related evidence, plausibility of mechanisms, study design and data quality, real world benefits, novelty, etc.) \citep{McShaneArxiv} and reporting of \emph{a priori} analysis of statistical power to avoid emphasis on implausibly large effects given low statistical power \citep[the ``winner's curse''][]{GelmanandCarlin2014, SzucsandIoannidis2017, Bernardietal.2017}.
 Additionally, we support the writing of statistical journals that chronicle all of the steps in the analytical process \citep{Kassetal.2016}, and clearly delineating the boundary between inferences based on \emph{a priori} hypotheses and discoveries from \emph{post hoc} data exploration.
